flo
Effective as of 6 September, 2024 

See the previous versions of our Privacy Policy here. This policy explains how we handle your personal data. Here’s a quick summary first, with key takeaways. It is not a substitute for reading the full policy, along with our Terms of Use.

Terms of use image
Safeguarding Your Data: Flo’s dedication to Privacy and Security
We are proud to hold two certifications for internationally recognised privacy and security standards. Flo has obtained independent certifications in both ISO/IEC 27001 in Information Security and ISO/IEC 27701 in Privacy. Our certifications demonstrate our commitment to maintain high standards when it comes to securing your information and managing a strong privacy programme. When you use Flo, you are trusting us with your personal data. We are committed to being transparent, protecting your rights, and respecting your data. 

Terms of use image
Anonymous Mode
Flo is the first female health app to introduce further privacy protections for your data with Anonymous Mode. With an even deeper layer of privacy, Anonymous Mode gives you the option to access the app without your name, email address, or technical identifiers being associated with the data you put into the app.

Terms of use image
Data that helps to serve you
When you use Flo, we collect your personal data and use it to improve your experience and service. We can then increase the safety and accuracy of your predictions and give you relevant app content and product offers.

Terms of use image
You can contribute to the growth of the Flo community
If you consent, we may use technical information about your device and other information about you (such as your device’s unique technical identifier, age group, subscription status, emails and the fact you launch the app) to reach you for promotional purposes.

Terms of use image
You’re in control and can reach out to us
We believe in transparent and open conversation - you can access, modify, correct, erase, and update your personal data by emailing us at support@flo.health or emailing our data protection officer at dpo@flo.health. Where we rely on your consent to process your personal data, you can withdraw your consent. If you have any questions about this Privacy Policy, let us know. 

Terms of use image
We limit children’s access to the app
You must be at least 13 years old to use the app (16 years old for European Economic Area, United Kingdom residents and Canada).

Introduction
This Privacy Policy explains how Flo Health UK Limited and its affiliated entities (“Flo” or “we” or “us”) complies with the provisions of the General Data Protection Regulation (“GDPR”), the UK GDPR and any other applicable data protection laws and regulations. This Privacy Policy explains how Flo collects, stores, uses, transfers, and shares personal data from our users (“you”) in connection with the Flo mobile application, Flo Period & Ovulation Tracker application (the “App”),* and the flo.health website, including all subdomains, products and services related to it (the “Website”) (all collectively, the “Services”). 

Flo Health UK Limited is a UK registered data controller of the Services.

*The App may be listed under a different name depending on your location. A full list of names is available here. 

We may change this Privacy Policy from time to time. If the changes are material, we will notify you by email or through the App. If permitted by law, your continued use of the Services after this policy has been updated indicates your acceptance of changes made. In some cases, you will be given a choice to accept changes to this policy. If you do not accept the terms of the updated Privacy Policy, please do not use the Services. 

The latest updates to this policy are available on our Website and in the App.

Personal data we collect from you
We collect personal data about you when you interact with the Services. This can be directly from you or from other sources and third parties. 

Personal data you provide to us directly:

General information: When you sign up to use the Services, we may collect personal data such as your name, email address, year and month of birth, password, place of residence and location information including time zone and language. We may be able to infer your sex and/or gender by your use of the Services. 

You may also choose to input information such as your first name or the name you would like us to call you. This is led by you and it will not affect your use of the Services should you choose not to enter this information. 

Well-being: When you use the Services, you can choose to input personal data about yourself, such as your weight; height; body mass index (BMI); body temperature; menstrual cycle dates; pregnancy and details relating to your pregnancy (if you select the pregnancy mode); other symptoms and stages that are related to your menstrual cycle; perimenopause and menopause symptoms; general well-being and health; symptoms, which may include information relating to your sex life; or other information, like your physical and mental well-being, water intake and sleep duration. 

Third-party services (including wearables): With your consent, you may also allow us to connect to third-party services, such as Apple HealthKit and Google Health Connect. This enables us to import information about your health and activities into the App without the need for you to log it yourself. This imported data may include fitness activities, weight, height, BMI, calories burned, heart rate, number of steps/distance traveled, body temperature, sleep and other activity data. This data provides you with general insights into your activities and helps us to make better predictions regarding your cycle. We will process this data in order to provide you with App functionality and features. Importing this data is subject to the Google Health Connect and Apple HealthKit privacy policies and terms. Please also check the applicable terms and privacy policies of the wearable devices that you may use to connect to Flo. Your wearable provider may collect usage data relating to your connection for its own business purposes, including to improve its services. 

Personal data we collect automatically:

When you access or use the Services, we may automatically collect the following information:

Device information: device model; information about the operating system and its version; unique device identifiers; enabled device accessibility features (e.g., display features, hearing features, and physical and motor features); mobile operator and network information; device storage information or version of your device system. 

Location information: IP address for an approximate location (not precise location); time zone or information about your mobile service provider.

Data about your use of the Services, including: frequency of use; areas and features of the Services that you access or use; payment transaction information (excluding full payment card details) or engagement with particular features.

To collect this and other information, we may use cookies and other similar technologies. See more in our Cookie Policy.

Data from external sources: we may receive personal data about you from third parties. For example, we may obtain information from third parties to enhance or supplement your existing information, including to customize your experience and for statistical purposes and analytics.

How we use your personal data
Depending on which features of the Services you use, we will process your personal data based on one or more of the following legal bases (we have included some examples):

Your consent: you can give us permission to process your health data to provide the Services.
To fulfill our contractual obligations to you in order to provide the Services to you: we may process your personal data to fulfill our contractual obligation to you for activities such as management of your Flo account and other administrative purposes.
Legitimate interest: we may process your personal data based on our legitimate interests in order to manage our Services better. For example, we may use your personal data in order to: 
identify and fix bugs;
determine genuine user interaction with the Services (rather than bots); 
monitor the App and analyze its performance and reliability; 
inform you of matters concerning your subscriptions;
conduct vulnerability scanning to protect the security of the Services; and 
review aggregated App usage trends.
Further examples of our legitimate interests are outlined in the table below. When relying on this legal basis, we first determine that we have a legitimate interest in conducting and managing our business. We then consider and balance potential impacts to you and your rights, to ensure that our interests do not override them. 

Legal obligation: We may be obligated to process some of your personal data to comply with applicable laws and regulations.
Below, we describe the purposes for which we process your personal data and our lawful bases for doing so, including some basic examples:

To support the existing functions of the App, including tailored content, insights and materials you see when you use the App based on: the data you provide within the App; the Services you have selected for use (e.g. your selected mode) and the App features you engage with; information obtained from connected third-party services (like Apple HealthKit and Google Health Connect); and certain information provided in onboarding questionnaires.

Consent
We use your cycle data to predict your future cycles or ovulation, analyze your data to provide you with new features and Services, and provide certain suggested articles or materials (e.g., stories, Health Assistant, and Secret Chats) to read. 
For the customization of product and service offerings and making our recommendations to you, for example through emails or push notifications, including for third-party products and offerings (excluding data from Apple HealthKit and Google Health Connect).
Consent
We may offer you a discount for Flo Premium.
To process transactions and send you related information, including confirmations and reminders for account management and other administrative purposes.
Contract
Using your device data, we may send you a reminder (e.g., via push notifications) if your subscription has expired or is due to expire, or we may send you an email containing your invoice, if applicable.
To respond to your comments, questions, requests and to provide customer service. 
Legitimate interest
We may process your name and email to reply to your support request or to contact you about a specific query or question you have raised.
To review App content, feedback and complaints raised to ensure clinical safety and medical accuracy of the App.
Legitimate interest
We may process your name and email to review support requests that require review by our medical team.
To send you: technical notices and updates; security alerts (and investigate incidents); support and administrative messages; and  customer satisfaction surveys.  

Legitimate interest
To request that you update your App to ensure you have access to the latest features. 
To integrate data between the Website and App in connection with onboarding users. Please note that information provided during your Website onboarding journey, and before you create a Flo account, will not be stored by Flo until your account is created. 

Legitimate interest
When you sign up for the Services on the Website, we use a third party, AppsFlyer, to help us identify you as an existing user when you use the App.
To monitor and analyze trends, usage and activities in connection with our App.
Legitimate interest
We may analyze your browsing activity in the App to ensure the App functions as it should in response to your interactions, fix issues and improve your future experience.
Promotional communications regarding our Services. 
Consent
If you give your consent and we use your personal data, we can post your review or comment on our Website.
Principles of processing
Data minimization and purpose limitation: We will not process personal data in a way that is incompatible with the purposes for which it has been collected or authorized by you or collect any personal data that is not needed for the mentioned purposes.

No sale of personal data: We will not sell or rent your personal data for monetary gain. We will not disclose your personal data except as otherwise described in this Privacy Policy. We will share your personal data with our service providers who support our Services as described in this Privacy Policy. We will also not use information received through your use of the Apple HealthKit or Google Health Connect framework for advertising or similar services, or sell it to advertising platforms, data brokers, or information resellers.

Your privacy rights
It does not matter what country, state, or region you come from; we are committed to providing you with individual privacy rights in accordance with the GDPR in relation to your personal data. 

What are these rights?

Only you or a person legally authorized to act on your behalf may make a verifiable request related to your personal data. We reserve the right to perform reasonable checks to confirm a person’s authorization, (for example, in the US, we may check if they are a person registered with the California Secretary of State).

Terms of use image
Correction of your personal data
If you believe that your personal data is inaccurate, you have the right to contact us and ask us to correct such personal data.

Terms of use image
Restriction of processing
You have the right to request that the processing of your personal data be restricted in some circumstances. For example, you have the right to request the restriction of your personal data if you contest the accuracy of your personal data and we need some time to verify such accuracy. 

Terms of use image
Access to your personal data
You have the right to request information about what personal data we process about you, to access all your personal data and to receive a copy of it, including in a structured and portable form (.json). For iOS Flo Premium users, the App also enables you to download a report containing some of your personal data from within the App. 

Terms of use image
Right to data portability
You have the right to request your personal data in a portable form which enables you to, for instance, reuse your data for your individual purposes or different services. In other words, it may allow you to move, copy or transfer personal data from Flo in a safe and secure way. 

Terms of use image
Erasure of your personal data
You have the right to request that we erase your personal data at any time. Please be aware that erasing some personal data may affect your experience using certain features of the Services that rely on historical data.

Terms of use image
Objection to the processing of your personal data
You have the right to object to the processing of your personal data, for example, if we process it for direct marketing purposes.

How to exercise your privacy rights
Please email us at support@flo.health to exercise your privacy rights. 

If you would like to exercise your right to request erasure of your account, you can visit the settings in your App. 

We will address your request within one-month after receipt. It can take us up to 90 days in some cases, for example, for full erasure of your personal data stored in our backup systems. We will let you know if we need more time and explain the reasons for the delay. 

We rely on your consent to process your health data to access the Services. You can withdraw this consent by contacting us or deleting your account in the App.

What else?
Please keep in mind that if we receive a vague request, we may contact you to better understand the request. We may also refuse to comply with or charge a reasonable fee for a request that is manifestly unfounded and/or excessive (repetitive) requests. 

We will require you to prove your identity. Normally, we will verify that the request is coming from the same email that you provided when registering. If you have not registered your account, we may ask you to undergo additional verification checks to ensure we can appropriately respond to you. 

Subject to applicable laws, you may have the right to lodge a complaint with your local data protection authority about any of our activities. If you have any concerns about our privacy practices, please let us know by emailing our support team at support@flo.health or by emailing our data protection officer at dpo@flo.health.

Third parties processing your personal data
We will not share your personal data with third parties except as specified within this Privacy Policy.

Promoting our Services
With your consent, we may share some of your non-health personal data with AppsFlyer to promote the Services. 

AppsFlyer is a mobile marketing platform that handles your personal data in accordance with our instructions. By using AppsFlyer and its integrated partners to promote the Services, we are able to reach you and people like you on various platforms and spread the word about Flo. If we need to share your personal data with other platforms for this purpose, except as we have explained in this Privacy Policy, we will ask for your consent. 

Here is a step-by-step illustration of how we work with AppsFlyer and its integrated partners for marketing and promotional purposes:

Single image
1. You become a Flo user, and with your consent, we start sharing the following personal data with AppsFlyer and its integrated partners to promote the Services: 

technical identifiers: IP address (which may also provide general location information), user agent, identifier for advertisers (IDFA), Android ID (in Android devices), Google advertising ID, customer-issued user ID, and other similar unique technical identifiers
your age group;
your subscription status; and
the fact of App launch.
2. Flo sends your personal data to AppsFlyer, which analyzes it and provides us reports and insights on how to optimize our promotional campaigns.

3. At the same time, AppsFlyer sends your personal data to some of its integrated partners (e.g., Pinterest, Google Ads, Apple Search Ads, Meta Audience and others) to find you or people like you on different platforms, including social media websites. 

These integrated partners analyze your personal data and show relevant information about Flo to people who might be potentially interested in it or remind you about revisiting the App if you stopped using it a while ago. 

Read more about how AppsFlyer works here and how its integrated partners work here. 

4. Opt-out options: You can withdraw your consent or opt out from the sharing of your personal data with AppsFlyer for marketing purposes in accordance with this subsection anytime by adjusting your device settings in iOS or Android.

Note that we also use AppsFlyer to integrate data between the Website and App in connection with onboarding users. You are not able to opt out of AppsFlyer’s processing of your personal data for these purposes.

Processing to make the App run 
In some situations, we engage other companies to process your personal data on our behalf. We refer to these companies or service providers as “processors.” 

Processors are companies that help us run the Services, support our communication with you, or perform other App-related activities. They process certain personal data on our behalf to accomplish the goals related to the App functions and deliver the Services. We remain responsible for any acts or omissions of our processors, and we enter into data processing contracts with them to the extent required by applicable law.

Flo’s team is based in a number of countries. The following group companies are therefore data processors within the Flo group of companies:

Flo Health Cyprus Ltd (based in Cyprus); 
Flo Health LTU UAB (based in Lithuania and our main EU establishment); and 
Flo Health NL. BV (based in the Netherlands).  
Here are some of the main processors we rely on:

Infrastructure and security
Amazon Web Services, Inc. 
AWS Privacy Notice
All personal data
Storage of all personal data when you use the App 
Infrastructure and security
Cloudflare, Inc.
Cloudflare Privacy Policy
All personal data
Security of the App, content delivery
Infrastructure and security
Auth0, Inc. (Okta, Inc.) 
Okta Privacy and Cookie Policy
Email address
IP address
Name
Authentication and authorization services
Infrastructure and security
Kibana (ElasticSearch) Inc.
ElasticSearch Inc. Privacy Statement
All personal data
To protect users’ data 
Infrastructure and security
Vercel Inc. 
Vercel’s Privacy Policy
Personal data processed via the Website
Improving the performance of the Website to ensure efficient service delivery
Email communications
SendGrid, Inc. (Twilio, Inc.)
SendGrid Privacy Notice
Email address
To reach you with our newsletters, surveys and notifications
Email and in-App communications
SurveyMonkey (Momentive Europe UC))
SurveyMonkey Privacy Notice
IP address
User ID
Results of surveys
To deliver different Service-related surveys
Analytical tools
Looker (Google Cloud EMEA, Ltd))
Looker Privacy Policy
App usage data
To understand how you use the App, engage with particular features and what you like or dislike the most
To generate statistical reports. 
Analytical tools
Databricks, Inc.
Databricks Privacy Notice
App usage data
To understand how you use the Website, engage with particular features and what you like or dislike the most to engineer product experiences
Analytical tools
Google LLC (Google Tag Manager & Google Analytics 4) 
Google Privacy Policy

Google Analytics 4: Data privacy and security

Website usage data
To monitor our performance and understand how you use the Services on our Website, while applying suitable privacy protections. 
Internal functions
Algolia SAS
Algolia Privacy Policy
IP address and user ID
Content of the search request
Age
Aim and usage purpose
To provide you search functions inside the App, including search suggestions for all users
Some personal data is needed to increase the accuracy of the search
Customer support
Zendesk Inc., USA
Zendesk Privacy Policy
Email address
Content of the emails
To process and sort all emails received from you
Customer support
Customer Thermometer Ltd 
Customer Thermometer Privacy Policy
Email address
Responses to surveys
To obtain customer feedback
Machine Learning Development Platform
Tecton, Inc.
Tecton Privacy Policy
Data relating to cycle dates, goals, symptoms
Providing you with predictions and App functionality
Payments
 
Apple, Inc.
Apple: App Store & Privacy Notice
Payment and banking information
Personal identifiers
To collect and process payments for subscription to the App
Payments
Google LLC, USA
Google Privacy Policy
Payment and banking information
Personal identifiers
To collect and process payments for subscription to the App
Payments
Stripe, Inc., USA
Stripe Privacy Policy
Payment and banking information
Personal identifiers
To collect and process payments for certain Website 
Payments
PayPal Inc.
PayPal Privacy Statement
Payment and banking information
Personal identifiers
To collect and process payments for subscription to the App
Payments
Chargeback Gurus (International Risk Mitigation, LLC)
Chargeback Gurus Privacy Policy
 
Payment and banking information
To handle disputes and process refunds 
User onboarding and data integration
AppsFlyer UK Ltd 
AppsFlyer Privacy Policy
Data relating to device model, language and operating system
To integrate data between the Website and App in connection with onboarding users
To create a link between accounts when utilizing Flo for Partners
To simplify, track and optimize influencers campaigns
For information relating to processors we engage to utilize cookies, please refer to our Cookie Policy. 

Aggregated information
We may aggregate, anonymize, or de-identify your personal data so that it cannot reasonably be used to identify you. We may share such data with third parties such as academic research institutions or use the data for statistical purposes. For example, we may share or use general age and demographic information and aggregate statistics about certain activities or symptoms from data collected to help identify patterns across users in articles, blog posts, and scientific publications. Sharing such data may contribute to the advancement of scientific research on female health. 

For certain targeted academic or user research studies, we will contact you and rely on your consent. You can withdraw your consent at any time by emailing us at dpo@flo.health.

Information posted by you
The App features several community areas like Secret Chats and guided groups where users with similar interests can share information and support one another. 

Posting your personal data in such groups is not permitted, and is in violation of our rules, such as the Secret Chats Rules. Any information (including personal data) you share in any online community area or online discussion is by its nature, open to the Flo community. Please think carefully before posting anything that may identify you in any public forum. Remember, what you post can be seen, disclosed to, or collected by others and may be used in ways we cannot control or predict, including to contact you for unauthorized purposes. If you mistakenly post personal data in our community areas and would like it removed, email us at support@flo.health. 

We may also preserve or share some of your personal data in the following limited circumstances: 
in response to subpoenas, court orders, or legal processes, to the extent permitted and as required by applicable law (including to meet national security or law enforcement requirements); 
when disclosure is required to maintain the security and integrity of the Services or to protect any user’s security or the security of other persons, consistent with applicable laws. In such cases, we may also delete some of your personal data (e.g., by resetting your password to avoid unauthorized access);
to assert legal rights or defend against legal claims; 
when disclosure is directed or consented to by the user who has inputted the personal data; 
in the context of an acquisition or transfer of any party of our business or in connection with the business reorganization; and
depending on the circumstance, we may rely on legitimate interest or legal obligation as our legal basis for the processing activities above.
Anonymous Mode
Anonymous Mode lets you create a Flo account without your email, name, or technical identifiers being associated with your new Anonymous Mode account. 

If you have an existing account, certain non-identifiable data will be transferred to your new Anonymous Mode account (e.g., your cycle data). Your old account with personal information you logged from your previous cycles will be automatically deleted in line with our retention policy, and you will no longer have access to it.

Limitations of Anonymous Mode: When you choose to create an Anonymous Mode account, some features of the App will not be available to you since they use personal data to function. These features may include integration with your wearable device, some push notifications and emails. 

When you create an Anonymous Mode account, we cannot identify you. While our customer support will not be able to answer some specific or technical questions, we will do our best to help. 

As is the case with all digital Services, in certain limited circumstances, it may be theoretically possible for someone to find a way around security measures. For instance, a user’s device may be utilized without authorization by a third party. Anonymous Mode accounts unlink all personal information from stored health data, which reduces the risks posed by such events. For more information about Anonymous Mode, please read our Anonymous Mode FAQs here.

Flo for Partners
If you are over 18 years old, you can select the Flo for Partners Service, in which you permit certain information from your Flo account to be shared with your partner. As the main user, you have full control over this sharing and can stop sharing at any time.  

What information will be shared with my partner?
Your partner will have read-only access to the information that you share. This means that they cannot download or edit your information. Your partner can not see or edit: your calendar information that was created prior to your decision to share; your personal notes; any symptoms or feelings that you have logged while using the App; or your interaction with other features in the App (such as Secret Chats).

If you’re trying to conceive or keeping track of your menstrual cycle, your partner will have access to a view-only version of your current cycle day and cycle phase predictions calendar. Your partner will also receive tailored daily educational insights and notifications during significant phases of your cycle. 

If you’re pregnant, your partner will receive regular updates about your pregnancy, including tailored daily educational insights. They will also receive notifications about any changes that may be happening to your body, symptoms commonly experienced and important development milestones. 

Your partner will be able to see within their App if you switch between modes - for example, if you switch from ‘track pregnancy’ to ‘track cycle’ their content will be adjusted accordingly. 

What data is collected from you as a partner? 

If you’re a partner and you are receiving information from the main Flo user, we will collect your name and email (in order to create a partner account with Flo) and your month and year of birth in order to verify your age. While your gender information is not directly collected, this is inferred by your use of the App. We will not collect any health data relating to you.

Retention of your personal data
Except as set forth below, we will retain your personal data for as long as needed to provide you with the Services or otherwise fulfill the purposes for which it was collected. 

Impact of account deactivation/requests to erase personal data: At any time, you can deactivate your account by following the steps detailed above at ‘How to exercise your privacy rights’. We will address your deletion request within one-month after receipt. It will take us up to 90 days in some cases to complete full erasure of your personal data stored in our backup systems. If you choose to deactivate your account, Flo will generally delete all your personal data, and it will not be recoverable should you later create another account. 

Impact of App deletion or inactivity: If you choose to delete the App from your device or your account becomes inactive, we will retain your personal data for a period of three years in case you decide to reactivate the Services or reinstall the App. After three years of inactivity, we will delete your personal information. While this is the Flo data retention standard, you can still ask for your data to be deleted at an earlier date by contacting us. The App covers different periods of users’ lifecycle; therefore, retention of your data is needed in some cases to secure your smooth experience with other App functions (e.g., switching to pregnancy mode after cycle tracking). 

Limitations: You should be aware that although we will delete, anonymize or otherwise de-identify your data where possible, we may retain certain personal data and other information after your account has been terminated or deleted. This is as required and permitted by applicable law, like the GDPR, and will include the following circumstances: 

as necessary to comply with legal obligations; 
establishment, exercise or defense of legal claims; and 
for archiving purposes in the public interest, scientific or historical research or statistical purposes.
How do we delete your data?
We use industry-standard methods and procedures to ensure that we securely and permanently delete your personal data from our systems so that it is no longer capable of recovery. These procedures can include automated notifications to some of our processors who process your personal data on our behalf.

Security of your personal data
General security measures
We implement technical and organizational measures in an effort to protect personal data from loss, theft, misuse, and unauthorized access, disclosure, alteration, and destruction, taking into account the nature of the personal data that we process and risks associated with special categories of personal data we collect. This includes:

encryption of your personal data in transit and in rest;
systematic vulnerability scanning and penetration testing;
protection of data integrity;
organizational and legal measures: For example, our employees have different levels of access to your personal data and only access your personal data for limited and necessary purposes required for the operation of the Services. We impose strict responsibility on our employees for any disclosure, unauthorized access, alteration, destruction, or misuse of your personal data; and
conducting periodical data protection impact assessments in order to ensure that the Services fully adhere to the principles of privacy by design, privacy by default, and others. We also commit to undertake a privacy audit in the event of Flo’s merger or takeover.
Please protect your password. Do not share it with others or allow anyone to use your mobile device. You may also wish to add a passcode or enable face ID to access the App for an added layer of protection. 

No security system is perfect. Therefore, we cannot guarantee the absolute security of the Services or that your information will not be intercepted while being transmitted to us.

Security breaches
If we learn of a security systems breach, we may either post a notice or attempt to notify you by email and will take reasonable steps to remedy the breach as specified in applicable law and this Privacy Policy. If we learn of a potential personal data breach, together with other actions referred to in the Privacy Policy, we will take actions to remedy the breach as appropriate under the circumstances, which may include logging you out from all the devices, resetting a password (sending a temporary password for you to apply), and performing other reasonably necessary activities.

If you want to report a security incident related to the Services, please email us at security@flo.health.

Children’s privacy
General age limitation: The Services are not intended for children, and we do not knowingly collect personal information from children under 13 years old through the Services. If you are aware of anyone under 13 years old using the Services, please email us at support@flo.health and we will take the required steps to delete such information and/or delete the child’s account. 

Age limitation for residents of the European Economic Area (EEA), United Kingdom (UK) and Canada: Due to legal requirements, we do not allow the use of the Services by residents of EEA or the UK younger than 16 years old. If you are aware of anyone younger than 16 using the Services, please email us at support@flo.health, and we will take steps to delete such information and/or delete the child’s account. 

Some App functions are only available to users over the age of 18 years.

Communication with you
We may contact you from time to time via email or through other means (like pop-ups or push notifications) to communicate with you about Services, offers, promotions, rewards, and events offered by us and provide news and information that we think will be of interest to you. These communications may be based on the Services you have selected for use (e.g. your selected mode) and the App features you engage with.

Opt-out options: You can always opt out of receiving marketing emails by unsubscribing via the “Unsubscribe” link contained in the email. Opting out of these marketing emails or notifications will not end the transmission of service-related emails that are necessary to your use of the Services. You may also opt out of receiving push notifications by adjusting your settings in your device. If required, we may ask some users to provide additional consent for such communications.

Please note that we may contact you with information about Services, offers, promotions, rewards, and events offered by us and others via third-party platforms (like social media). 

Presence on social networks 

We may use social media platforms to promote Flo and engage with our customers. When you interact with us on these platforms, we may process information, such as your username, profile picture, and any comments or posts you make related to Flo, for engagement purposes only.

Storage and international personal data transfers
Flo is based in the UK. Personal data we collect is transferred to and processed in the US; where it is governed by US law) and to other countries (where it is governed by the applicable laws of those countries). These transfers are usually cloud-based, and can occur when you engage with the Services and are subject to our retention policies. The laws of other countries may not offer the same protections as the laws of your jurisdiction.

Transfers of personal data outside of the EEA and the UK

Personal data in the EEA and the UK is protected by the GDPR and the UK GDPR. When transferring personal data outside of these locations, we will always apply appropriate safeguards in accordance with the law to ensure your personal data is protected. For example, we enter into data transfer agreements that incorporate the European Commission approved Standard Contractual Clauses and carry out transfer risk assessments.

For further information, please email us at support@flo.health.

Data Privacy Framework (“DPF”) participation
As set forth by the US Department of Commerce, Flo complies with the EU–US DPF, the UK extension to the EU–US DPF, and the Swiss–US DPF (collectively, the “DPFs”). We have certified to the US Department of Commerce that in reliance of the DPFs, we adhere to the DPFs’ principles when processing personal data of individuals within the European Union, United Kingdom, and/or Switzerland. For onward transfers, Flo is responsible for processing personal data we receive under the DPFs and then transfers to a third party acting on Flo’s behalf. Flo remains liable under the DPFs if those third parties process personal data in a way that is not in compliance with the DPFs, unless Flo can prove that we are not responsible for the cause of any damage.

If there is any conflict between the terms in this Privacy Policy and the DPFs’ principles, the DPF principles will govern. You can view our certification here.

Complaints and dispute resolution: We commit to resolve complaints about our collection and use of your personal data. EU, UK, and Swiss individuals with inquiries or complaints regarding our DPFs should first contact us by emailing us at dpo@flo.health or by mail using the address Flo Health UK Limited, Fourth Floor, International House, 1 St Katharine’s Way, London, E1W 1UN, United Kingdom. 

Arbitration: You may also be able to invoke binding arbitration for unresolved complaints, but prior to initiating such arbitration, a resident of a European country (including Switzerland) participating in the DPFs must first (1) contact us and afford us the opportunity to resolve the issue; (2) seek assistance from JAMS; and (3) contact the US Department of Commerce (either directly or through a European data protection authority) and afford the Department of Commerce time to attempt to resolve the issue. If such a resident invokes binding arbitration, each party shall be responsible for its own attorney’s fees. Please be advised that pursuant to the DPFs, the arbitrator(s) may only impose individual-specific, nonmonetary, equitable relief necessary to remedy any violation of the DPFs with respect to the resident. The arbitration option may not be invoked if the individual’s same claimed violation of the principles (1) has previously been subject to binding arbitration; (2) was the subject of a final judgment entered in a court action to which the individual was a party; or (3) was previously settled by the parties.

We are subject to the investigatory and enforcement powers of the US Federal Trade Commission concerning personal data transferred under the DPFs, the United Kingdom’s Information Commissioner’s Office (for UK individuals), the relevant EU Data Protection Authority, and the Swiss Federal Data Protection and Information Commissioner for resolving disputes with Swiss individuals. 

We have further committed to refer unresolved DPFs complaints to JAMS, an alternative dispute resolution provider located in the United States. If you do not receive timely acknowledgment of your complaint from us, or if we have not addressed your complaint to your satisfaction, please contact JAMS or visit https://www.jamsadr.com/DPF-Dispute-Resolution for more information or to file a complaint. The services of JAMS are provided at no cost to you.

United States
We do not sell your information for monetary gain.

Under certain state laws (including California), if we disclose personal information to a third party for any benefit, this can be considered a “sale” or “share” or personal information, even if the third party does not use the personal information for any other purpose. We “share” personal information if we disclose personal information to a company for purposes of cross-context behavioral advertising. 

Request to opt out/Do Not Track: We do not sell your personal information. You have the right to opt out of sharing your personal information with our analytics and advertising partners. This includes opting out of “sale” — a term very broadly defined under US state legislation (including California) — and “Do Not Track” requirements. Note: This personal information will not contain your health data. Regardless of your choices, we do not share health data with these partners.

Do Not Track is a web browsing setting that adds a signal to your browser header that tells other websites that you do not want their tracking cookies. Flo currently does not respond to such signals in browsers because no DNT standard has been adopted. To exercise this right you can contact us at support@flo.health. 

Limiting the use of sensitive personal information: Sensitive personal information that we process is limited to only those purposes that are necessary to provide Services to you.

Request to know/access: In addition to the other rights mentioned in this policy, you have the right to request to know (i) the personal and sensitive information we have collected about you and our purposes of use; and (ii) the categories, sources, and third parties involved in personal information we have collected about you or “sold” or disclosed in the past 12 months. You may exercise your right to request to know twice a year, free of charge.

Shine the Light: California residents may also request information from us once a calendar year about any personal information shared with third parties for their own direct marketing purposes. We don’t share information with third parties for their own marketing uses, but please email us at support@flo.health if you have questions. You’ll need to specify “California Privacy Rights Request” in the subject line of the email, and also include your name, street address, city, state, and ZIP code. 

References to “personal data” in this policy include “sensitive/personal information” as defined under California laws.

Contact us
General

If you have any questions or concerns about your privacy, you may contact us or our data protection officer by writing to us at:

Flo Health UK Limited, Fourth Floor, International House, 1 St Katharine’s Way, London, E1W 1UN, United Kingdom

Flo Health LTU UAB, Saltoniškių street 2 Vilnius, LT-08126, Lithuania (our main EU establishment)

Or by emailing us at support@flo.health or dpo@flo.health.


CLUE
Clue Privacy Policy
Last updated July 22, 2025

1. How Clue values data privacy
At Clue, we believe that technology and data present a groundbreaking opportunity to empower people to take control of their health. The Clue app gives people the ability to understand what is going on inside of their bodies and minds based on individual tracked health data, providing self-insight and self-advocacy that’s powered by data processing.

We also fully acknowledge the responsibility that comes with being the safekeepers of so much intimate data which is tracked by people using Clue. Which is why we are always striving to achieve the highest standards of privacy and security. Keeping your data safe is at the core of everything we do.

We see it as our job to be clear and transparent so that you can truly understand what we do with your data, even though the digital ecosystem of an app is complex. To provide our service as a health app, we rely on a number of other providers as summarized below to help us.

Please read the whole of this Privacy Policy to understand how we handle your data. We have done our best to make it as clear and comprehensible as possible. If you have any questions, reach out to us at <trust@helloclue.com>.

If you are a US resident, you can read our Supplemental US Privacy Notice here.

2. The types of data we process
We process three types of data in order to provide our services on the Clue app and the helloclue.com website. All of our data is securely stored on servers located in the European Union (EU).

Account data: In order to create your Clue account, we process some of your personal data such as a username, date of birth and email address.

Usage data: In order to provide our services and technically improve performance, we process how you interact with our products using different data points. Such data includes device data, which informs us about the device you use to access our app services (such as device model, name and identifiers, device settings, application identifier, crash information). On our website, we also collect information about your browser (such as browser settings, operating system, system settings). Other usage data includes the IP address provided by your browser or mobile device, which we collect in order to deliver the service to your device. We also use the IP address to determine your approximate location for statistical and analytics purposes, and for regulatory compliance in different countries. We do not collect your precise location.

Health data: In order to provide our service as a health app, we process health data and other sensitive data that you choose to track in the Clue app. Such health data may include your cycle information (e.g. period length, pain, or spotting), and depending on the data you provide, it may also contain other sensitive data about your experiences (e.g. weight, body temperature, hair quality, sexual intercourse). We only process the health data you choose to share with the Clue app via tracking. You may use different methods provided by the app to track your health data in the app. This can include manually entering your data into the app, or importing your data from other integrations or devices supported by Clue (such as Apple Health or fitness trackers).

3. How and why we process your data
Data processing is essential to providing the service of Clue. Whenever you use our services, some personal and non-personal data is collected, stored, and analyzed using internal and third-party tools.

Below are the purposes for which we process your data, and the type of data that’s processed to fulfill each purpose:

3.1 To provide our core service to you
To provide our service, we process the following:

Health data: This is processed whenever you track your health data in the Clue app, either manually or through import integrations, in order to provide our core service as a health tracking app. This includes both your cycle information data and other sensitive data that you choose to track in the Clue app.
Device data, event data, usage data, IP address: This is processed when you use the Clue app or helloclue.com, to understand how you interact with our services and to technically improve performance.
Account data: This is processed when you set up your Clue account in the app or in the website, to enable you to sign in to the Clue app, and additionally to communicate with you on service-related topics. Such communications may include information about your account, essential app updates, or insights and recommendations based on health data you have tracked. These communications can be sent to you via in-app messages, reminders, notifications, or emails.
Please read the following sections to understand which third party services, integrations, and partnerships we use to provide our core service.

3.1.1 Essential third party providers:
We use several third party providers to help us perform our core services.

Amazon Web Services: Clue uses Amazon Web Services EMEA SARL (“AWS”) as our hosting provider to store our data on secure servers. We only use AWS data centers in the European Union. All data stored with AWS is encrypted by Clue.

Braze: Clue uses services operated by Braze, a company based in the United States, to help us facilitate communication with you via in-app messages, push notifications and emails. Such communications may include information about your account, essential app updates, or insights and recommendations based on health data you have tracked. For this purpose Braze processes your email address, name, user identifier, certain tracked health data, and usage data. This data is always treated in a masked, obfuscated (pseudonymized) form.

Braze has ensured an adequate level of data protection by being listed under the EU-US Data Privacy Framework ,and by also entering into an agreement with Clue based on the Standard Contractual Clauses for data transfer between EU countries and non-EU countries (see Section 4). The privacy policy of these services can be found on their respective websites. Data concerning your use of the Clue app is stored on a server in the EU, operated by Braze, Inc.

It is not possible to opt-out of Braze as it is an essential tool that we require in order to provide our services to you. However, you can opt out of certain types of messaging from Braze, as explained in Section 3.6.

Datadog: Clue uses services provided by Datadog Inc. (Datadog), a company based in the United States, to carry out service and infrastructure monitoring and alerting. Datadog helps us monitor the application performance in real time and resolve issues impacting our users quickly. Datadog stores the data on EU servers.

It is not possible to opt-out of Datadog as it is an essential tool that we require in order to provide a functioning Clue app to you.

Firebase (Android users only): Clue uses a suite of performance analysis and monitoring tools called Firebase, which is provided by Google Inc. Firebase allows us to monitor the overall performance and stability of our app, implement internal version control, identify bugs and prioritize fixes. For this purpose Firebase collects your IP address, device identifier, as well as event and usage data related to your use of Clue. This data will be transferred to and stored on a server in the EU and operated by Google, LLC.

It is not possible to opt-out of Firebase as it is an essential tool that we require in order to provide a functioning Clue app to you.

Sparkpost: Clue uses services provided by Message Systems Inc. (“SparkPost”), a company based in the United States, to process names, email addresses and personal information that may be included in transactional emails (such as “I lost my password” or “Verify your Clue account” emails).

It is not possible to opt-out of Sparkpost as it is an essential tool that we require in order to provide a functioning Clue app to you.

3.1.2 Integrations to track your data:
In addition to manually tracking your health data in the Clue app, importing data from other sources is supported for the integrations listed below.

Apple Health (iOS): This section is only applicable to users who choose to sync their Apple Health app with the Clue app. Clue will not exchange any personal data with Apple’s Health app unless you specifically approve this. Approval can be given by you in the relevant settings of the Health app or within the Clue app via your Settings. If you have given your approval, Clue may interact with the Health app on your iOS device and read and/or write information between the Clue app and the Health app. This may include a transfer of your personal data to Apple servers located outside the European Union.

You can choose if and to what extent your personal data is exchanged between Clue and the Health app by granting or revoking the relevant permissions in your Health app settings. This can be done at any time. Please refer to the Privacy Information of Apple Health for further information.

Oura Ring: This section is only applicable to users who sign up to Clue via Oura, or who already have a Clue Plus account and have decided to connect their Clue account with their Oura Ring. Clue will not exchange any personal data with Oura. If you have connected your Oura profile with your Clue profile and given permission in your Oura App settings, Oura shares some pseudonymized tracked data with us. We use this for the purpose of providing better data visualization and enhancing your Clue app experience.

You can choose if and to what extent your personal data is exchanged between Oura and Clue, by granting or revoking the relevant permissions in your Oura settings. This can be done at any time. You can read more about this in Oura’s Privacy Policy.

3.1.3 Social logins:
When first creating your Clue account, there are several options on how to sign up. In addition to signing up with your email address, it’s possible to use services provided by Facebook, Apple, or Google.

Facebook Login: Clue uses “Facebook Login” to allow users to sign in to their Clue account with their Facebook credentials. If you use this service, you authorize us to collect your basic profile information from Facebook, such as your name, email address and profile picture. This information is collected by Facebook and is provided to us under the terms of Meta’s Privacy Policy. You can control the data we receive from Facebook in the privacy settings within your Facebook account.

If you signed up to Clue using Facebook,Clue will only exchange with Facebook the types of data you provided to Facebook when creating an account with them (such as name, email address). This may include a transfer of your personal data to Facebook servers located outside the European Union. It is your choice if and to what extent you use the “Facebook Login” service and what information you provide to Facebook. Absolutely no health data will be exchanged with Facebook.

Sign in with Apple: Clue uses “Sign in with Apple” to allow users to create and sign in to their Clue account with their Apple credentials.

If you sign up to Clue using Apple, Clue will exchange certain data with Apple like device data, IP-address, and information you provided to Apple when creating an account with Apple Inc. This may include a transfer of your personal data to Apple servers located outside the European Union. It is your choice if and to what extent you use the “Sign in with Apple” service and what information you provide to Apple. Absolutely no health data will be exchanged with Apple for the purpose of using the “Sign in with Apple” service.

Sign in with Google: Clue uses “Sign in with Google” to allow users to create and sign in their Clue account with their Google credentials. If you use this service, you authorize us to collect your basic information from Google, like your email address. You can manage this any time in your Google account. Please see Google's resources for more details on this.

If you sign up to Clue using Google, Clue will exchange with Google the types of data you provided to Google when creating an account with them (such as name, email address). This may include a transfer of your personal data to Google servers located outside the European Union. It is your choice if and to what extent you use the “Sign in with Google” service and what information you provide to Google. Absolutely no health data will be exchanged with Google.

3.1.4. Partnerships
To allow users from other platforms to sign up to Clue and subscribe to Clue Plus, Clue has partnerships with those listed below.

Wellhub: This section is only applicable to users who sign up for Clue Plus via Wellhub. Clue has partnered with Wellhub (formerly Gympass), a health and wellbeing platform located in the United States, that enables its members to access many health and wellbeing services. Clue Plus is part of their service offering.

If you choose to sign up for Clue Plus using your Wellhub subscription, Wellhub sends Clue your Wellhub ID as confirmation that you are a Wellhub subscriber. Upon receiving this information, Clue will then activate your Clue Plus subscription. Clue shares with Wellhub whether you have been active in the Clue app. This is done by sending an event called ‘Create Record’ to Wellhub. At no point does Wellhub ever receive any of your tracked health data.

Legal basis: Our legal basis for processing the above mentioned data is Art. 6 b) General Data Protection Regulation (GDPR), which means that we use it to perform the contract that you have entered into with Clue, via Wellhub. We also process your Clue account data and usage data on the legal basis of Art 6 Sec.1 lit b) GDPR to provide our services to you. The processing of health data to provide our service to you is based on the following consent according to Art 9 Sec.2 lit a) GDPR:

I agree to Clue processing the health data I choose to share with the app, so they can provide their service.

All personal data collected for providing our service is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.1.5. Payment provider
If you decide to subscribe to Clue Plus via helloclue.com, your subscription will be handled by our payment provider, Paddle, who will facilitate the payment. In this case, Paddle will become the controller of your payment data. Clue will remain the controller for all the data related to the usage of the Clue app. Paddle will never have access to any of your tracked data or other app related usage data. You can read more about how Paddle handles your payment data in their Privacy Policy.

3.2 To provide customer service
To help a Clue user who has contacted our Support Team with questions regarding our services, we may communicate with this person via email to provide customer service. Providing this service is part of our paid Clue Plus subscription.

If you use this service, Clue will have to access and process your personal data, including your health data depending on the nature of your query. We do this so we can adequately provide you support with your request.Third party providers:

To provide customer support and communicate with you, Clue uses services from Slack Technologies Ltd (“Slack”), based in Ireland, and Zendesk, Inc. (“Zendesk”), based in the United States. We also use Growthdot, a company based in Ukraine, to anonymise customer support communications at the end of the retention period.

Whenever data is transferred to providers outside of the European Economic Area (EEA), we always apply the appropriate safeguards as outlined by the General Data Protection Regulation (GDPR) (see Section 4).

Legal basis:The legal basis for processing your account data and usage data for customer service is Art 6 Sec. 1 lit b) GDPR, and Art 9 Sec.2 lit a) GDPR for your health data.

When you contact the Clue Support Team, you explicitly provide your consent for the processing of your personal data, including your health data, so that your query can be answered.

All personal data collected for our customer service is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.3 To help advance scientific research
To help advance menstrual and reproductive health studies, we share relevant de-identified health data you’ve tracked in the Clue app with carefully selected research partners to be used in their scientific studies.

When you track in Clue, your data becomes something powerful. It can help answer questions to better understand menstrual and reproductive health. Women and people with cycles are still widely underrepresented in health research. We believe that the data tracked in Clue can change this. By teaming up with our trusted research partners we can advance research, break harmful taboos and lay the groundwork for better healthcare.

We only share data that is directly relevant to the research question and follow strict protocols to ensure your data always remains anonymous to the researchers. We use a de-identification technique which means all personal identifiers like your name and email address are erased. Your dataset is then assigned a random ID, making sure you can’t be identified by the researchers.

If you are a participant in a scientific study that is run by a research facility using Clue as a tool to collect information for that study, then Clue will share your personal information with the research facility only under the terms of your consent as given to that research facility. When you use Clue as part of a scientific study, we will otherwise treat your personal data with the same care as we do all user data. The research facility will be solely responsible for the usage of your personal data, including health data, in the context of their scientific study. We consider that Clue and our partnered research facilities have joint responsibility ("joint controllership" under GDPR) in this case.

Research partners: We team up with carefully selected research partners both in and outside of the European Union. You can read more about the type of research partnerships we have here.

Whenever data is transferred to partners outside of the European Economic Area (EEA), we always apply the appropriate safeguards as outlined by the General Data Protection Regulation (GDPR) (see Section 4).

Legal basis: The processing of your health data for scientific research is based on the following consent according to Art 9 Sec.2 lit a) GDPR, if you have toggled this on in your privacy settings:

I agree to the health data I track in the app being de-identified and shared with carefully selected research partners in and outside of the European Union to advance menstrual and reproductive health studies.

You can toggle this off at any time. All personal data collected for scientific research is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.4 To improve Clue features with health analytics
To help us build more valuable features in Clue, we process health data you’ve tracked in the app to better understand which features are most useful to you. By processing data such as period dates and cycle experiences, we can better understand how our community uses the app and further tailor the experience to fit their needs.

By analyzing how our community uses the app, we can understand which features are most valuable. We use these insights to drive feature development, so we can make sure to deliver what’s most important. This could include things like improving the accuracy of predictions, building new algorithms to offer you more health insights, or creating content about topics we see our community wants to read about more.

The processing of health data for analytics purposes is managed internally by Clue. We store your data on servers in the EU and it’s always de-identified, removing personal identifiers like your name and email address. These procedures ensure your privacy.

Third party providers: We do not use any third party providers for this purpose.

Legal basis: The processing of your health data for health analytics is based on the following consent according to Art 9 Sec.2 lit a) GDPR, if you have toggled this on in your privacy settings:

I agree to the health data I track in the app being processed for analytics purposes so Clue can improve my predictions, develop new algorithms and create more valuable features with personalized insights.

You can toggle this off at any time. All personal data collected for the health data analytics is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.5 To technically improve the Clue app
To help us improve the Clue app experience, we process and analyze certain data so we can improve the app and make features easier to use. This includes usage data like your device ID and IP address.

By improving the app and its technical platform, we can deliver a better experience for you and the wider Clue community. It allows us to tailor the app to different types of devices, and most importantly, strive to make the app experience the best it can be.

Third party providers: We do not use any third party providers for this purpose.

Legal basis: We process your usage data on the legal basis of Art 6 Sec.1 lit f) GDPR to technically improve the Clue app based on Clue’s legitimate interest as a company to continuously improve the app and deliver an improved service to you. We do not believe there is anything you could have against this. However you can always opt out of this data processing at any time in your Clue app’s privacy settings by toggling off:

As outlined in Clue’s Privacy Policy and based on Clue’s legitimate interest as a company to continuously improve the app, certain usage and technical data is processed. I have the right to opt out of this at any time.

All personal data collected to technically improve the Clue app is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.6 To allow recommendations from Clue
To make personalized recommendations, we process certain usage data to understand how you interact with the Clue app, as well as the health data you’ve tracked to deliver you more personalized insights. This includes data such as your period dates and cycle experiences. We also collect your account data so we can then send you these recommendations via in-app messages, emails, and push notifications (if you’ve enabled permissions on your device). By personalizing your experience, we can provide information that’s more tailored to you and your needs. This might look like sending you updates about new Clue features based on what you’ve tracked, or suggesting interesting products from partnerships we support that may be relevant to you. For example, if you’re trying to conceive, we might recommend services that can support you on your conception journey. We strive to be mindful about what we communicate and how often, as providing you with the most comfortable experience possible is our main priority.

Third party providers: We use certain third party software providers to help us send these updates, such as Braze (see Section 3.1.1). These providers are not permitted to use the data for any other purpose other than to help Clue personalize your experience.

Whenever data is transferred outside of the European Economic Area (EEA), we always apply the appropriate safeguards as outlined by the General Data Protection Regulation (GDPR) (see Section 4).

Be assured that the sensitive health data you track in the Clue app is never shared with or sold to advertisers, or any partners whose services we may recommend in Clue.

Legal basis: The processing of your account data and usage data for recommendations from Clue is based on the following consent according to Art 6 Sec.1 lit a) GDPR, and the processing of health data for recommendation from Clue is based on the following consent according to Art 9 Sec.2 lit a) GDPR, if you have toggled this on in your privacy settings:

I agree to my account data, usage data and health data I track in the Clue app being processed so Clue can send me personal recommendations for relevant products based on my tracked experiences. Certain third-party providers, including some located outside of the European Union, are used to help with this.

You can toggle this off at any time. All personal data collected for providing personal recommendations is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.7 To help Clue optimize their advertising efforts
To help us analyze how Clue’s advertising performs, we process certain types of usage data (for example when you install the Clue app or subscribe to Clue Plus) and technical data including your device ID and IP address. This helps us identify whether you’ve already downloaded Clue or have a Clue Plus subscription, and find out which Clue ads you interacted with (if any).

By doing this, we can optimize our advertising efforts. For example, if you’ve already downloaded the Clue app, we won’t show you an ad to download Clue. It also helps us understand on which platforms people find out about us, and learn what kind of Clue advertising performs best. With better advertising, we can help raise awareness about the Clue app and empower more people to take charge of their health.

Third party providers: We use certain third party services to help us with our advertising efforts. These include Apple Search Ads and Google Ads, both based in the United States, and Adjust and Taboola (described in more detail below).

Adjust: Clue uses services operated by Adjust, a company based in Germany, to measure and improve campaign performance through attribution and analytics. They help us understand where our users are coming from, which age group they are from, and how they are interacting with our app, so that we can optimize our ad campaigns. Adjust uses your advertising identifier (Apple IDFA on iOS, Google Play Services ID on Android), and your IP addresses to provide us these insights. Through Adjust, we share standard app events like installation of the Clue app or subscription to Clue Plus services with certain advertisement networks like Meta and Tiktok. We do this to avoid showing you Clue ads if you’ve already downloaded or are subscribed to Clue Plus. Adjust does not have access to any of the personal health data you track in the app, and therefore cannot share this sensitive information with any advertisement networks the platform corresponds with. Adjust does not have access to any of the personal health data you track in the app. You can read more about how Adjust handles data in their Privacy Policy
Taboola: Clue uses an advertising service by Taboola, a company based in Germany. They allow us to find new users through their ad platform and optimize our advertising efforts by better understanding where our users come from. With their service, we can identify if users visited specific Clue website landing pages via Clue advertisements hosted by Taboola. This is done by adding a Taboola pixel to our Clue landing pages, and Taboola placing cookies on our website (see Section 7.2). The pixel is a small file that saves information about the visiting user’s device, operating system, and IP address. This is done only if the person agreed to our website’s analytical cookies. The data is pseudonymized in this process. You can read more about how Taboola handles data in their Privacy Policy.Whenever data is transferred outside of the European Economic Area (EEA), we always apply the appropriate safeguards as outlined by the General Data Protection Regulation (GDPR) (see Section 4). Be assured that the sensitive health data you track in the Clue app is never shared with or sold to advertisers. We do share a minimal amount of technical data with advertising networks, as described above, so that you won’t see a Clue ad if you’ve already downloaded the app or subscribed to Clue Plus.
Legal basis: The processing of your usage data to promote Clue is based on the following consent according to Art 6 Sec.1 lit a) GDPR, if you have toggled this on in your privacy settings:

I agree to my usage and device data being processed so Clue can optimize their advertising efforts to more effectively tell more people about Clue. Certain third party providers, including some located outside of the European Union, are used to help with this.

You can toggle this off at any time. All personal data collected to help to promote Clue is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.8 To optimize advertising with activity tracking (iOS users only)
To help us optimize our advertising and to spread the word about Clue, we enable activity tracking on iOS devices when permissions are turned on. Activity tracking means that limited technical data (like your device ID) and usage data (for example installing Clue or subscribing to Clue Plus) is shared with advertisers so you don’t see Clue ads that aren’t relevant to you. You can turn off activity tracking any time in your iOS Settings.Activity tracking is strictly limited to technical and usage data. Your health data is never shared with advertisers and always protected.

Legal basis: The processing of your usage data for activity tracking is based on the following consent according to Art 6 Sec.1 lit a) GDPR, if you selected “Allow” when presented the following prompt from Apple:

Allow “Clue” to track your activity across other companies’ apps and websites?

All personal data collected for activity tracking is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.9 To optimize our advertising efforts and to improve helloclue.com with website analytics
To optimize our advertising efforts and to improve our website, we process usage data such as your IP address and device data. This helps us track the performance of our website, understand how you use our website, and offer you an improved experience. For this purpose we use cookies and third party tracking services. Cookies are small text files that are intended to make the site better for you to use.

In general, cookies are used to retain preferences, store information for things like shopping carts, provide tracking data to third-party applications like Google Analytics, Taboola or Outbrain, or identify your device for special advertising purposes such as retargeting. You can learn more about the specific cookies and tracking services used on helloclue.com in Section 7.

Legal basis: The processing of your usage data for website analytics is based on the following consent according to Art 6 Sec.1 lit a) GDPR:

By using our website you consent through an opt-in in the cookie banner that Clue may use cookies and third-party services, and collect your usage data under a unique identifier for the purposes of tracking, analysis, and improvement of our website, as well as advertising purposes such as showing you relevant Clue content.

The usage of non-essential cookies on our website is based on a consent according to § 25 of the German Act on Data Protection in Telecommunication and Digital Services (TDDDG). When visiting our website, you can decline the use of non-essential cookies in the pop-up notification. If you consent to the non-essential cookies, you may withdraw your consent again at any time in your browser’s cookie settings.

All personal data collected for website analytics is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.10 To deliver Clue newsletters
To provide newsletter and email services, we process certain contact data of those people who have opted in so we can send such communications.

If you’ve registered for a newsletter service of Clue, without being a Clue app user with an account, we will process your information provided in the registration on helloclue.com. This may include your name and email address, which is needed to send you the newsletters you’ve subscribed to.

If you’re a Clue app user with an account, Clue will process the email address you provided with your account registration to send you the newsletters you’ve subscribed to, as well as occasional emails with promotional content. The content of these communications will be for similar Clue services to what you use, or may include promotion for third party products which may be relevant to you from partnerships we support.

If you’ve requested Cycle Review emails as part of your Clue Plus subscription, then that email will also contain a summary of personal health data that you have tracked in the app.

Third parties: Clue may share information such as your email address to third-party providers for the sole purpose of carrying out our newsletter services. Our current provider for this service is Braze. For more information about Braze, see Section 3.1.1. Whenever data is transferred outside of the European Economic Area (EEA), we always apply the appropriate safeguards as outlined by the General Data Protection Regulation (GDPR) (see Section 4).

Legal basis: The legal basis for sending you our newsletter is based on your consent according to Art 6 Sec.1 lit a) GDPR. The legal basis for promotional emails is based on Art 6 Sec.1 lit a) and lit f) GDPR. The legal basis for Cycle Review emails is based on your consent according to Art 9 Sec.2 lit a) GDPR.

You can unsubscribe from our newsletters, promotional emails, and Cycle Review emails at any time by clicking the unsubscribe link at the bottom of the emails.

All personal data collected for providing our newsletter services is deleted by us as soon as it is no longer required for the purpose for which it was collected.

3.11 To gain insights from surveys and interviews
To receive feedback from the Clue community, Clue may use surveys and run interviews to gain insights on certain health topics, the performance of the app, or the value of features. Any information given by you via such surveys is processed by Clue for the purposes as set forth in this Privacy Policy.

Third party providers: Clue uses easyfeedback GmbH “Easyfeedback", a survey tool provider based in Germany, to run surveys and process results. They may process data from surveys you choose to participate in for science research, user experience research, or customer satisfaction research. In case personal data is processed for a survey, you will be asked for an explicit consent. Your Clue app data is never shared with Easyfeedback.

Clue also uses UserTesting, a provider located in the United States, for conducting user experience studies. If you’re invited to sign up to a study pool via a Clue survey, you’ll be taken to the UserTesting website and be asked to provide your name and email to enter the pool. The selection of participants is carried out by UserTesting, therefore, we cannot guarantee that you will be invited to participate in a further study or interview.

Legal basis: The legal basis for the processing of your personal data in a survey is your consent according to Art 6 Sec.1 lit a) GDPR. In case health data is involved, the legal basis is Art 9 Sec.2 lit a) GDPR.

All personal data collected for the provisioning of our surveys and interviews is deleted by us immediately as soon as it is no longer required for the purpose for which it was collected.

4. Data transfer outside the European Union
Any personal data collected from you may only be transferred to countries outside the European Economic Area (EEA) if we observe applicable privacy regulations and ensure that your privacy rights remain protected.

To ensure an adequate level of data protection in accordance with Art 46 GDPR, we have entered into Standard Contractual Clauses with all non-EEA third parties whose data processing tools we use (data processors) if there is no adequacy decision by the EU Commission for their particular country. For U.S. based data processing, we also use third-party providers that are certified under the EU-US Data Privacy Framework as a guarantee under Art 46 GDPR.

You can read more about the Standard Contractual Clauses here. The Standard Contractual Clauses help us to implement an adequate level of data protection between Clue and our processors, who must agree to follow strict data protection rules. However, they do not bind the governmental bodies of the non-EEA country in which our processor operates. In some cases, governments may have powers of surveillance that run contrary to EU law data protection principles.

We choose our processors very carefully. We do not work with processors based in countries where we are concerned about the rule of law with respect to privacy. We follow the guidance of the European Data Protection Board on additional contractual and technical measures to ensure a sufficient level of privacy in different situations.

5. Your data protection rights
We believe that privacy—including data privacy—is a basic human right. At Clue we strive to ensure that your rights are respected.

Here are some key facts about your privacy that we would like you to know:

i. Our products and services have been designed to collect only the data necessary to provide our services. We only collect and process your data for the purposes outlined above and detailed in this Privacy Policy.

ii. The security of our servers is routinely verified by experts to protect your data from unauthorized access. You can contact us at <trust@helloclue.com> if you have any questions about the security of our services.

iii. We do not retain your data in an identifiable format for longer than necessary to deliver our services.

iv. Clue does not engage in any automated decision-making or profiling activities.

As a user of the Clue app and website, you may exercise your rights under the EU General Data Protection Regulation (GDPR) to:

i. Request information on your personal data processed by Clue. Upon your request, this information will be provided to you electronically. You can contact us to request your information at <trust@helloclue.com>.

ii. Gain access to your information by requesting a copy of your data in a format that is readable by other companies or organizations (data portability). iii. Correct your personal information and health data in the app settings and in the tracking categories available in the Clue app.

iv. Withdraw your consent from ongoing data processing at any time by deleting your account (for details see the Support section of the Clue app, under “Account Questions”), changing your privacy preferences in Settings, and/or unsubscribing from our newsletter or other email communications by clicking the link at bottom of the email.

v. Request the complete deletion of your data, including all past data sent to third-party services used for tracking and analysis, by reaching out to <trust@helloclue.com>. Your data will be deleted within 1 month.vi. Lodge a complaint with the relevant supervising authority if you believe Clue is processing your personal data in violation of applicable data protection regulations.

6. Data security procedures
Protecting your data privacy is at the core of what we do. We apply security measures to protect against misuse, loss, and/or alteration of personal information under our control. We follow industry standards when transferring and storing your data. Though we cannot ensure or guarantee that misuse, loss or alteration of information will never occur, we use all reasonable efforts to prevent it.

6.1 How Clue secures your personal data
When you create an account with Clue, your personal profile data is stored separately from your health data and your service settings. Doing this means your health data has an even higher level of protection. Clue uses servers located in the European Union to process and store your personal data.

When you create your Clue password, it’s stored using one-way encryption with both “hashing” and “salting” techniques. This means your password is combined with a random string of characters and then scrambled up so it's unreadable. Not even Clue staff have access to your password. Doing this ensures extra protection for your password. Note that if you use social login to create your account (see Section 3.1.3), Clue does not receive your original password.

When your data is sent between your device and our Clue servers, we use hypertext transfer protocol secure (HTTPS). This is a type of encrypted data transmission, which scrambles the information being sent so it’s unreadable. Doing this increases the security of your data transfer. HTTPS is the same technology used to create secure connections for your web browser and is indicated by a padlock icon in the URL bar of your browser.

When you subscribe to Clue Plus, all your payment information is securely processed by the Apple App Store or Google Play Store. Clue does not store your payment information at any time.

6.2 Clue’s recommendations for protecting your data
Usually, the biggest threat to the security and privacy of your data is that someone—probably someone you know—gains access to any of your devices without your consent. The data you enter into Clue is private and it should stay that way. If you actively choose to share your data, for example if you are using Clue Connect, make sure to regularly review whether it still makes sense for you to share that information with your connections. Here are some tips on how to keep your devices secure:

Protect your Clue account: Make sure to create a unique long password for your Clue account. We recommend using a password manager for this purpose.

Protect your device:

i. Activate either passcode, TouchID, or FaceID authentication for your device. This automatically secures your Clue data and prevents any person from using your device without your permission.

ii. Set up a feature that will allow you to erase all the data from your device if it’s been lost or stolen.

For iOS, activating this feature is a two-step process. First, activate “Find My iPhone” (instructions here) and then enable “Erase your device” (instructions here). For Android, set up Find My Device and, if needed, use the connected web interface to lock or wipe your phone remotely.

7. Cookies on helloclue.com
For the purpose of improving our advertising efforts, tracking the performances of our services and to improve Clue, we use cookies on our helloclue.com website. For more information on this purpose and its legal basis, please see Section 3.9.

Cookies are small text files that are intended to make the website better for you to use. In general, cookies are used to retain preferences, store information for things like shopping carts, provide tracking data to third-party applications like Google Analytics, or identify your device for special advertising purposes such as retargeting.

We use third-party analytics and tracking services to help us measure the performance of our website. Whenever data is transferred outside of the European Economic Area (EEA), we always apply the appropriate safeguards as outlined by the General Data Protection Regulation (GDPR) (see Section 4). Be assured that the sensitive health data you track in the Clue app is never shared with or sold to advertisers. We do share a minimal amount of technical data with advertising networks, for example, so that you won’t see a Clue ad if you’ve already downloaded the app or subscribed to Clue Plus.

Such third parties and services are listed below.

7.1 Google Analytics - Website
Our website uses Google Analytics, a web analysis service operated by Google LLC. (“Google”). Google Analytics uses cookies (text files) stored on your computer to allow for analysis of your visits to websites and interactions with them in order to personalize your experience and improve our services. Information produced via cookies will be transferred to and stored on a server in the USA operated by Google. You can find out more about Google Analytics here.

The following Cookies are used by Google Analytics:

Cookie Name	Value (example)	Purpose	Expiration
_ga	2.1326744211.152311160746-5	This cookie is written to the browser upon the first visit. It is included in each page view request and used to distinguish unique users on the website.	2 years
_gid	2.1687193234.152311160746-1	This cookie is used to group the user behavior for each user.	24 hours
_gat_gtag_UA_property-id	1	This cookie is used to throttle the rate at which requests are sent to Google Analytics so as to increase the efficiency of network calls.	1 minute
Google analyzes this information to offer reports to Clue on website usage and online usage of associated services. Under the terms of Google's analytics service, Google may also transfer this information to third parties, either when this is required by law or when third parties are contracted by Google to process this data. Google must not allow your IP address to be linked to any other personal data. By opting in via the cookie banner on Clue's website, you consent to data being used and processed by Google as described above. You can withdraw consent for this use of your data at any time. Please note that this withdrawal only applies to future activities.

7.2 Taboola
Clue uses an advertising service by Taboola, a company based in Germany. Taboola allows us to find new users through their ad platform and optimize our advertising efforts by better understanding where our users come from. With their service, we can identify if users visited specific Clue website landing pages via Clue advertisements hosted by Taboola. This is done by adding a Taboola pixel to our Clue landing pages, and Taboola placing cookies on our website (only if the person agreed to our website’s analytical cookies).

Taboola uses the following cookies:

Strictly necessary cookies:

Cookie Name	Purpose	Expiry
taboola_session_id	Creates a temporary session ID to avoid the display of duplicate recommendations on the page.	session
Sitecountrycode	Maintains a record of the user’s country code for site speed performance.	
siteState	Maintains a record of the user’s US state for legal compliance purposes.	
Functionality cookies:

Cookie Name	Purpose	Expiry
taboola_fp_td_user_id	Indicates that the user clicked on an item that was recommended by Taboola’s Services. This is used for reporting and analytics purposes	1 year
t_gid	Assigns a unique, partitioned User ID that Taboola uses for attribution and reporting purposes, and to tailor recommendations to this specific user based on interactions with one advertiser or publisher.	1 year
t_pt_gid	Assigns a unique User ID that Taboola uses for attribution and reporting purposes, and to tailor recommendations to this specific user.	1 year
trc_cookie_storage	Assigns a unique User ID that is used for attribution and reporting purposes.	1 year
_tb_t_ppg	Used on websites of Taboola’s publisher Customers that utilize the Taboola Newsroom services. It maintains a session reference about the user’s visit to this particular website.	30 minutes
Performance analytics cookies:

Cookie Name	Purpose	Expiry
GA_Count_Countries__c	Purpose: Counts the number of different countries a certain user was browsing from	
GA_Last_Device_Category__c	Saves the user’s device type (Mobile/Desktop).	
tb_click_param	Used on websites of our publisher Customers that utilize the Taboola Newsroom services. It measures performance of the publisher’s homepage articles that are clicked..	50 seconds
taboola global:last-external	Used for attribution purposes to see what link or page led a user to the current page.	Local Storage (deleted when the user deletes it)
global:last-external-referrer	Used for attribution purposes to see what link or page led a user to the current page.	Local Storage (deleted when the user deletes it)
You can read more about Taboola’s Cookie Policy here.

7.3 Outbrain
Clue uses an advertising service by Outbrain, a company based in the USA. Outbrain allows us to find new users through their ad platform and optimize our advertising efforts by better understanding where our users come from. With their service, we can identify if users visited specific Clue website landing pages via Clue advertisements hosted by Outbrain . This is done by adding an Outbrain pixel to our Clue landing pages, and Outbrain placing cookies on our website (only if the person agreed to our website’s analytical cookies).

Outbrain uses the following cookies:

Advertising Cookies:

Cookie Name	Purpose	Expiry
opout	Holds information about optout from Outbrain personalized advertising	1 year
obsessionid-{}	Stores a unique identifier of the session so that we don’t show only the same recommendations on the same session	30 minutes
recs-{}	Stores the recommendations we’re recommending so that we don’t show only the same recommendations on the same page	1 minute
ref-{}	Stores the referring document information to identify the source of traffic to improve contextual recommendations	1 minute
Personalized Advertising Cookies:

Cookie name	Purpose	Expiry
auid	Holds the advertising ID of the User on mobile devices. Used for tracking user actions, such as pages visited and clicks on recommendations, and personalized advertising	90 days
obuid	Holds the Outbrain UUID. Used for tracking user actions, such as pages visited, clicks on recommendations, and personalized advertising	90 days
outbrain_dicbo_id	Used for conversion attribution when a browser does not allow third party cookies 	1 day
Third Party Advertising Cookies:

Cookie name	Purpose	Expiry
Google Advertising Products	Cookie syncing	13 months
You can read more about Outbrain’s Cookie Policy here.

7.4 Snowplow
Our website uses Snowplow, an open source technology hosted by Clue, for collecting usage data that helps us understand how visitors interact with our websites in order to improve our services. You can find more about Snowplow here.

Snowplow uses the following cookies:

Cookie name	Value (example)	Purpose	Expiry
_sp_id	 *****-f1a5a44646f1.1712751362271.11	Stores user information that is created when a user first visits a site and updated on subsequent visits.	2 years
_sp_ses	*	Used to identify if the user is in an active session on a site or if this is a new session for a user (i.e. cookie doesn't exist or has expired). 	30 minutes
sp	N/A	Stores a server-side collector generated unique identifier for a user that is sent with all subsequent tracking event events.	1 year
Local storage:

Cookie name	Purpose	Expiry
snowplowOutQueue_{namespace}_post2 	Used to store a cache of unsent events. This is used to reduce the chance of events to be lost due to page navigation and events not being set to the collector before the navigation event occurs. Where GET requests are used, this key will end in _get rather than _post2	Local Storage (deleted when the user deletes it)
snowplowOutQueue_{namespace}_post2.expires	Used to match the concept of cookie expiry within local storage. This ensures a consistent behavior between cookie and local storage. Where GET requests are used, this key will end in _get rather than _post2	Local Storage (deleted when the user deletes it)
You can read more about Snowplow’s Cookie Policy here.

8. Young users of Clue
Clue does not knowingly collect or use personal data from children under the age of 16. When creating a Clue account, you are required to confirm that you are at least 16 years old or that your parents have agreed that you can use the Clue app.

If you are located in the EU, you can only use our services if you are over the relevant age at which you can provide explicit consent to the processing of your data under the laws of your country (e.g if you are at least 16 years old in Germany), or if you have the consent of your parent or legal guardian.

If you are a parent and learn that your child is using Clue without your permission, or if you have a specific question about data privacy at Clue, do not hesitate to get in touch with us at <trust@helloclue.com>.

If you are located in the United States, you cannot use the Clue app if you are under 13 years old. If Clue gains actual knowledge that information has been collected from children under the age of 13 in the United States contrary to the Children’s Online Privacy Protection Act of 1998 and the regulation thereunder, Clue will not disclose this data and reserves the right to immediately delete the account and wipe all related information, including health and sensitive data of the user, from our servers.

9. Changes to this Privacy Policy
Clue reserves the right to amend this Privacy Policy from time to time to reflect changes in the law, our data collection and data use practices, the features of Clue’s services, or advances in technology.

Please check this page periodically for changes and refer to the “last updated” date at the top of the page to know if it has been revised since your last visit. If we make any changes to this Privacy Policy that we consider to be material to your consent, we will notify you of them.

10. Responsibility for Clue’s data processing
Clue is made in Berlin, Germany, and the way we handle data meets the high standards set by German and European Union legal requirements. Clue is made by BioWink GmbH, Adalbertstraße 7-8, 10999 Berlin. Further contact information can be found here. Clue has an appointed data protection officer. Please do not hesitate to reach out to <trust@helloclue.com> if you have any questions.

11. Prevailing language of this Privacy Policy
Clue is used by women and people with cycles around the world. This wider Clue community accesses the Clue app in a multitude of different languages. We use professional translators and proofreaders to translate all of our communications, including this Privacy Policy, as accurately as possible into those languages.

However, please understand that we cannot assure 100% accuracy for all of our translations, in particular with respect to any legal content. Please note that the English version of this Privacy Policy is therefore the original version, which prevails over all other versions in case of deviation from the English original. The most up-to-date version of this Privacy Policy is always available in English on our website.

GLOW
Glow Privacy Policy
Effective date: Nov 4, 2024. View the previous version here.
We take your privacy very seriously. This Privacy Policy describes the
information and privacy practices of Upward Labs Holdings, Inc.
(“Glow,” “we”, “us” or “our”) and how we handle personal information
that we collect through our websites and mobile applications that link to
this Privacy Policy (collectively, the “Service”), as well as through social
media, our marketing activities and other activities described in this
Privacy Policy. This Privacy Policy also describes your choices and
rights with respect to your personal information.
We may provide additional, different or supplemental privacy notices for
specific products, services, or other business activities that we offer or
in which we are engaged. For example, if you enroll in a US study that
we conduct, we may provide you with a privacy notice that governs how
your personal information may be collected, used, and shared in
connection with the study.
You can download a printable copy of this Privacy Policy here.
Index
Personal information we collect
How we use your personal information
How we share your personal information
Your choices
Other sites and services
Security
International data transfer
Children
Changes to this Privacy Policy
How to contact us
California privacy rights notice
Notice at Collection
Notice of Right to Opt-Out of Sale/Sharing of and the “Do Not Sell or
Share My Personal Information” Link
Right to Opt-Out of Sale/Sharing of and the “Do Not Sell or Share My
Personal Information” Link
Notice to European users
Cookie notice
Personal information we collect
Information you provide to us. The specific personal information we
collect will depend on which Glow app you use and the features you
choose to interact with. Not all of the features described in this Privacy
Policy are available on every Glow app and certain categories of
personal information described in this Privacy Policy are relevant to only
certain Glow apps. Personal information you may provide to us through
the Service or otherwise includes:
Account data that you provide to create an account on the Service,
including your name, email address, password, date of birth and
mobile phone number.
Profile data that you chose to add to your profile on the Service,
such as your name, profile photo, location (e.g., city, state,
country), ethnicity, gender, relationship status, interests, preferred
language, occupation and insurance type.
Health data that you choose to provide:
directly through the Service, such as information about your
physical attributes, sexual orientation, fertility, pregnancy,
sexual activity, menstrual activity, sleep activity, mood, health
conditions, medications, and number of children; and
through your mobile health apps, such as Apple HealthKit,
Samsung Health, Google Fit, MyFitnessApp, which may include
any information you chose to store in those apps, subject to
your preferences for those apps.
Data about others, such as
the names and contact details of the spouses, partners or
caregivers to whom you choose to grant access to information
in your Glow app;
information in the Glow app of anyone who has granted you
access to it;
the names and contact details of health care providers with
whom you chose to share information in your account via
emails generated through the Service;
the email address of anyone you invite to use the Service
through features in the Service, and the name of anyone who
sent you such an invitation; and
information that you chose to share about your children, which
may include their name, date of birth, ethnicity, height, weight,
other physical attributes, photos, feeding activity, sleep
activity, developmental milestones, health and medications.
Communications that we exchange with you, including when you
contact us with questions or feedback, through social media, or
otherwise.
Payment and transactional data needed to complete your orders
on or through the Service (including name, address, payment card
information, billing information), and your transaction history.
Marketing data, such as your preferences for receiving our
marketing communications and details about your engagement with
them.
User generated content that you upload, generate, transmit, or
otherwise make available on the Service, such as profile pictures,
photos, videos, images, music, videos, comments, questions,
messages, your “likes”, as well as associated metadata. Metadata
includes information on how, when, where and by whom a piece of
content was created or collected, how that content has been
formatted or edited, and the location associated with the creation of
the content.
Other data not specifically listed here, which we will use as
described in this Privacy Policy or as otherwise disclosed at the
time of collection.
Third party sources. We may combine personal information we receive
from you with personal information we obtain from other sources, such
as social media accounts that you use to log into or connect to the
Service, which will allow us to collect the information you chose to make
available in your settings on that social media account.
Automatic data collection. We, our service providers, and our business
partners may automatically log information about you, your computer or
mobile device, and your interaction over time with the Service, our
communications and other online services, such as:
Device data, such as your computer’s or mobile device’s operating
system type and version, manufacturer and model, browser type,
screen resolution, RAM and disk size, CPU usage, device type (e.g.,
phone, tablet), IP address, unique identifiers (including identifiers
used for advertising purposes), language settings, mobile device
carrier, radio/network information (e.g., WiFi, LTE, 3G), and general
location information such as city, state or geographic area.
Online activity data, such as pages or screens you viewed, how
long you spent on a page or screen, the website you visited before
browsing to the Service, navigation paths between pages or
screens, information about your activity on a page or screen,
access times, and duration of access, and whether you have
opened our marketing emails or clicked links within them.
Cookies. Some of our automatic data collection is facilitated by cookies
and similar technologies. For more information, see our Cookie Notice.
Data about others. Users of the Service may have the opportunity to
refer friends or other contacts to us and share their contact information
with us. Please do not refer someone to us or share their contact
information with us unless you have their permission to do so.
How we use your personal
information
We use your personal information for the following purposes or as
otherwise described at the time of collection:
Service delivery. We use your personal information to:
provide, operate, and improve the Service and our business;
establish and maintain your user profile on the Service;
refer your contacts to join the Service;
communicate with you about the Service, including by sending
announcements, updates, security alerts, and support and
administrative messages;
understand your needs and interests, personalize your experience
with the Service and our communications; and
provide support for the Service, and respond to your requests,
questions and feedback.
Research and development. We may use your personal information for
research and development purposes, including to analyze and improve
the Service and our business. As part of these activities, we may create
aggregated, de-identified or other anonymous data from personal
information we collect. We make personal information into anonymous
data by removing information that makes the data personally identifiable
to you. We may use this anonymous data and share it with third parties
for our lawful business purposes, including to analyze and improve the
Service and promote our business.
Marketing and advertising. We, our service providers and our third
party advertising partners may collect and use your personal
information for the following marketing and advertising purposes:
Direct marketing. We may send you Glow-related or other direct
marketing communications as permitted by law.
Interest-based advertising. We may engage third-party advertisers
or advertising companies to display ads on our Service and other
online services. These companies may use cookies and similar
technologies to collect information about your interaction (including
the data described in the automatic data collection section above)
over time across the Service, our communications and other online
services, and use that information to serve online ads that they
think will interest you. This is called interest-based advertising. We
may also share names, email addresses and device identifiers of
our users with these companies to facilitate interest-based
advertising to those or similar users on other online platforms. You
can learn more about your choices for limiting interest-based
advertising in the Your choices section of our Cookie Notice.
As discussed above, we also may use your information to better
provide our services to you and to provide a more personalized
service to you, as detailed below.
Promotional Offers. From time to time, we may alert you to offers being
made by third parties, and if you choose to access those offers, we will
forward such information as you authorize us to share to those third
parties, and we may get compensated for doing so. In this instance, we
are acting merely as a conduit transferring your contact information, due
date and other specifically approved information to the relevant sponsor
on your behalf and at your specific instruction.
Compliance and protection. We may use your personal information to:
comply with applicable laws, lawful requests, and legal process,
such as to respond to subpoenas or requests from government
authorities;
protect our, your or others’ rights, privacy, safety or property
(including by making and defending legal claims);
audit our internal processes for compliance with legal and
contractual requirements and internal policies;
enforce the terms and conditions that govern the Service; and
prevent, identify, investigate and deter fraudulent, harmful,
unauthorized, unethical or illegal activity, including cyberattacks
and identity theft.
Retention. We generally retain personal information to fulfill the
purposes for which we collected it, including for the purposes of
satisfying any legal, accounting, or reporting requirements, to establish
or defend legal claims, or for fraud prevention purposes. To determine
the appropriate retention period for personal information, we may
consider factors such as the amount, nature, and sensitivity of the
personal information, the potential risk of harm from unauthorized use or
disclosure of your personal information, the purposes for which we
process your personal information and whether we can achieve those
purposes through other means, and the applicable legal requirements.
When we no longer require the personal information we have collected
about you, we may either delete it, anonymize it, or isolate it from further
processing.
How we share your personal
information
We may share your personal information with the parties below, with
other third parties with your consent, and as otherwise described in this
Privacy Policy or at the time of collection.
Other users and the public. Your name, profile URL, and any location or
profile photo that you choose to add to your profile are visible to other
users of the Service and the public by default, but you can choose to
make your profile private in your account settings. Unless you elect to
hide them in your settings, your posts on the Service will be visible to
other users of the Service and the public. This information may be seen,
collected, used and shared by others, and we are not responsible for
their collection, use or sharing of this information.
Third party apps. You may instruct us to share certain of your personal
information with third party apps such as Samsung Health, Apple
Healthkit, Google Fit and MyFitnessApp. These parties will use your
personal information as described in their respective privacy policies,
which are hyperlinked here: Samsung’s privacy policy, Apple’s privacy
policy, Google’s privacy policy and MyFitnessApp’s privacy policy.
Affiliates. Glow, Inc., and our affiliates, for purposes consistent with this
Privacy Policy.
Service providers. Companies and individuals that provide services on
our behalf or help us operate the Service or our business (such as
hosting, information technology, customer support, email delivery,
marketing, and website analytics) to facilitate the provision of such
services.
Payment processors. Any payment card information you use to make a
purchase on the Service is collected and processed directly by our
payment processors, such as Stripe. Stripe may use your payment
information as described in its privacy policy: https://stripe.com/privacy
Advertising partners. Third party advertisers and advertising
companies for the interest-based advertising purposes described above.
Advertisers whose ads are posted on our Service may be able to infer
information about you when you click on those ads (e.g., that you have a
newborn if you click on an ad about a newborn product).
Professional advisors. Professional advisors, such as lawyers, auditors,
bankers and insurers, where necessary in the course of the professional
services that they render to us.
Authorities and others. Law enforcement, government authorities, and
private parties, as we believe in good faith to be necessary or
appropriate for the compliance and protection purposes described
above. California has recently enacted AB 1242 which prohibits
companies whose principal executive office are in California from
providing records, information, facilities, or assistance in accordance
with the terms of a warrant, court order, subpoena, wiretap order, pen
register trap and trace order, or other legal process issued by, or
pursuant to, the procedures of another state or a political subdivision
thereof that relates to an investigation into, or enforcement of, a
Prohibited Violation. A Prohibited Violation “Prohibited Violation” means
any violation of law that creates liability for, or arising out of, either of
the following: (i) Providing, facilitating, or obtaining an abortion that is
lawful under California law; or (ii) Intending or attempting to provide,
facilitate, or obtain an abortion that is lawful under California law.
Business transferees. Acquirers and other relevant participants in
business transactions (or negotiations for such transactions) involving a
corporate divestiture, merger, consolidation, acquisition, reorganization,
sale or other disposition of all or any portion of the business or assets
of, or equity interests in, Glow or our affiliates (including, in connection
with a bankruptcy or similar proceedings).
Your choices
You have the following choices with respect to your personal
information.
Access or update your information. If you have registered for a Service
account with us, you may review and update account information by
logging into the account.
Delete your data. You may request to delete the personal information
you have provided through the Service by emailing privacy@glowing.com.
and we will complete the deletion within thirty days.
Delete your “Key Health Data” from our servers, but keep it on your
personal device. You may opt into our “Offline Data Protection” feature.
If you choose to do so, we will delete all “Key Health Data” (e.g., period
data, health logs, etc.) from our servers, but leave it on your personal
device. You will then be the only person with access to these health data
and no one else. The definition of “Key Health Data” will vary depending
on the App you are using, and we will define it as you opt into Offline
Data Protection. You should be aware, however, that opting into this
feature may cause certain features of our Apps to be limited. We will
define the limited features at the time you opt into the Offline Data
Protection Feature.
Delete your Glow account. You may request to delete your Glow
account by emailing privacy@glowing.com.
Revoking your consent. If we have asked for your consent or affirmative
authorization to collect, use or share your personal information, you can
revoke it either in the relevant privacy settings in your Glow app or by
emailing us at privacy@glowing.com. If, notwithstanding the choices
available to you as described in this “your choices” section, you wish to
revoke your authorization for Glow to handle your personal information
as described in this Privacy Policy, you may do so by requesting that we
delete your Glow account and the personal information that you have
provided through the Service by emailing us at privacy@glowing.com. We
will process such requests within a reasonably prompt timeframe after
receipt and your revocation will become effective once processing is
complete, until which time we will continue to handle your personal
information as described in this Privacy Policy
Opt-out of marketing communications. You may opt-out of marketingrelated emails by following the opt-out or unsubscribe instructions at the
bottom of the email, or by contacting us. You may continue to receive
service-related and other non-marketing emails.
Opt-out of personalized ads. You can opt-out of personalized ads on
our apps and tracking for interest-based advertising purposes by using
the disable personalized ads feature in your settings.
Cookies. For information about cookies employed by the Service and
how to control them, see our Cookie Notice.
Mobile device permissions. You can use your mobile device’s privacy
settings to disable our access to any data granted through them, such
as your device’s precise geolocation, contacts and photos.
Do Not Track. Some Internet browsers may be configured to send “Do
Not Track” signals to the online services that you visit. We currently do
not respond to “Do Not Track” signals. To find out more about “Do Not
Track,” please visit http://www.allaboutdnt.com.
Third party platforms. If you choose to connect to the Service through
your social media account, you may be able to use your settings in your
account with that platform to limit the information we receive from it. If
you revoke our ability to access information from a third party platform,
that choice will not apply to information that we have already received
from that third party.
Legal rights. You may have certain legal rights with respect to your
personal information. See the California privacy rights notice or the
Notice for European users for information about the rights available to
individuals in those locations. If you would like to exercise other legal
rights not described in this Privacy Policy, contact us
at privacy@glowing.com.
Declining to provide information. We need to collect personal
information to provide certain services. If you do not provide the
information we identify as required or mandatory, we may not be able to
provide those services.
Other sites and services
The Service may contain links to websites, mobile applications, and
other online services operated by third parties. In addition, our content
may be integrated into web pages or other online services that are not
associated with us. These links and integrations are not an endorsement
of, or representation that we are affiliated with, any third party. We do
not control websites, mobile applications or online services operated by
third parties, and we are not responsible for their actions.
Security
We employ a number of technical, organizational and physical
safeguards designed to protect the personal information we collect.
However, security risk is inherent in all internet and information
technologies and we cannot guarantee the security of your personal
information.
International data transfer
We are headquartered in the United States and may use service
providers that operate in other countries. Your personal information may
be transferred to the United States or other locations where privacy laws
may not be as protective as those in your state, province, or country.
Children
The Service is not intended for use by children younger than 16 years of
age. If we learn that we have collected personal information through the
Service from a child under 16 without the consent of the child’s parent or
guardian as required by law, we will delete it.
Changes to this Privacy Policy
We reserve the right to modify this Privacy Policy at any time. If we make
material changes to this Privacy Policy, we will notify you by updating
the date of this Privacy Policy and posting it on the Service. If required
by law we will also provide notification of changes in another way that
we believe is reasonably likely to reach you, such as via email or another
manner through the Service. Any modifications to this Privacy Policy will
be effective upon our posting the modified version (or as otherwise
indicated at the time of posting). In all cases, your use of the Service
after the effective date of any modified Privacy Policy indicates your
acceptance of the modified Privacy Policy.
How to contact us
Upward Labs Holdings, Inc.
580 California St
Suite 1200
San Francisco, CA 94104
United States of America
privacy@glowing.com
California privacy rights notice
This section applies only to California residents. It describes how we
collect, use, and share Personal Information of California residents in our
capacity as a “business” under the California Consumer Privacy Act
(“CCPA”) and their rights with respect to that Personal Information. For
purposes of this section, “Personal Information” has the meaning given
in the CCPA but does not include information exempted from the scope
of the CCPA. In some cases we may provide a different privacy notice to
certain categories of California residents, such as job applicants, in
which case that notice will apply instead of this section.
The following California Notice at Collection (including the section on
Privacy Rights following the chart below) and this Privacy Policy govern
the personal information we collect from California residents (“you”) on
any website or mobile application on which a link to this notice appears
and any personal information we collect in connection with delivering
services to you, whether online or offline. We have adopted this notice
to comply with the CCPA. Please take the time to read and understand
this California Notice at Collection. Please also read our entire Privacy
Policy which includes important information regarding how we collect,
use and share your personal information.
Notice At Collection
Like many companies, we use services that help deliver interest-based
ads to you, as we have described above. Our use of some of these
services may be classified under California law as “Sharing” of your
Personal Information from which you have the right to opt-out as
described below in our Notice of the Right to Opt-Out of the Sale/Sharing
of Your Personal Information.
Personal information that we collect, use and disclose. The chart
below summarizes the Personal Information we may collect by reference
to the statutory categories of Personal Information specified in the
CCPA, and describes our practices currently and during the 12 months
preceding the effective date of this Privacy Policy. The categories of
personal information, sources, purposes of collection/use/disclosure
and third parties listed in the chart below are described in more detail
above. Information you voluntarily provide to us, such as in free-form
webforms, may contain other categories of personal information not
described below.
Statutory category
PI we collect in this
category
Source of
PI
Business/commercial
purpose for
collection/use/disclosure
Categories of
third parties to
whom we
Categories of
third parties to
whom we
“disclose” PI for
a business
purpose*
“share” or “sell”
PI
Sensitive Personal
Information
Personal information that
reveals:
– A user’s account log-in
– A user’s racial or ethnic
origin,
– The contents of a user’s
mail, email, and text
messages unless the
Company is the intended
recipient of the
communication.
– Medical
InformationPregnancy Status
– Profile data
– Health data
– Data about others
– Personal information
collected and analyzed
concerning a user’s health.
– Personal information
collected and analyzed
concerning a user’s sex life or
sexual orientation.
– You
– Third
party
sources
– Service delivery
– Research & development
– Compliance & protection
– Third party
apps (with your
consent)
– Other users
and the public
(with your
consent)
– None
Identifiers
– Account data
– Profile data
– Data about others
– Device data
– You
– Third
party
sources
– People
you
authorize
Automatic
collection
– Service delivery
– Research & development
– Marketing & advertising
– Compliance & protection
– Affiliates
– Payment
processors
– Advertising
partners
– Business and
marketing
partners
– Other users
and the public
– Advertising
partners to
facilitate online
advertising
(device data
only)
California Customer Records
(as defined in California Civil
Code section 1798.80)
– Account data
– Profile data
– Health data
– Payment transactional data
– User-generated content
– Data about others
– You
– People
you
authorize
– Service delivery
– Research & development
– Marketing & advertising
– Compliance & protection
– Affiliates
– Payment
processors
– Other users
and the public
(with your
consent)
– None
Commercial Information
– Payment transactional data
– Marketing data
– Communications
– Online activity data
– You
– Automatic collection
– Service delivery
– Marketing & advertising
– Compliance & protection
– Affiliates
– Payment
processors
– Advertising
partners
– Business and
marketing
partners
– Advertising
partners (to
facilitate online
advertising)
Financial Information
– Payment transactional data
– You
– Service delivery
– Compliance & protection
– Payment
processors
– None
Internet or Network
Information
– Marketing data
– Device data
– Online activity data
–
Automatic
collection
– Service delivery
– Research & development
– Marketing & advertising
– Compliance & protection
– Affiliates
– Payment
processors
– Advertising
partners
– Third party
app
– Advertising
partners (to
facilitate online
advertising)
Geolocation Data
– General location associated
with IP address
–
Automatic
collection
– Service delivery
– Research & development
– Marketing & advertising
– Compliance & protection
– Affiliates
– Advertising
partners
– Business and
marketing
partners
– Other users
and the public
– Advertising
partners (to
facilitate online
advertising)
– Business and
marketing
partners (to
facilitate online
advertising and
offers to users)
Inferences
May be derived from your:
– Profile data
– Payment & transactional
data
– Marketing data
– User-generated content
– Online activity data
N/A
– Service delivery
– Research & development
– Marketing & advertising
– Affiliates
– Advertising
partners
– Advertising
partners (to
facilitate online
advertising)
Protected Classification
Characteristics
– We do not intentionally
collect this information but it
may be revealed in identity
data or other information we
collect
N/A N/A N/A None
Audio Visual Information
– Profile data
– User-generated content
(images, video or audio)
You Service delivery Affiliates None
*We may also share the categories of personal information described above with our professional
advisors, authorities and others and business transferees as described above in How we share your
personal information.
Data Retention. As discussed above, we generally retain personal
information to fulfill the purposes for which we collected it, including for
the purposes of satisfying any legal, accounting, or reporting
requirements, to establish or defend legal claims, or for fraud prevention
purposes. To determine the appropriate retention period for personal
information, we may consider factors such as the amount, nature, and
sensitivity of the personal information, the potential risk of harm from
unauthorized use or disclosure of your personal information, the
purposes for which we process your personal information and whether
we can achieve those purposes through other means, and the
applicable legal requirements.
When we no longer require the personal information we have collected
about you, we may either delete it, anonymize it, or isolate it from further
processing.
Your California privacy rights. As a California resident, you have the
rights listed below. However, these rights are not absolute, and are
subject to limitations and exemptions. In certain cases we may decline
your request as permitted by law.
Notice of Right to Requests to Delete, Requests to Correct, and
Requests to Know
Right to Information, Access, Correction and Deletion.
Information. You have the Right to Know what personal information
we have collected about you, including the categories of
information detailed below. You can request the following
information about how we have collected and used your Personal
Information on or after January 1, 2022:
The categories of Personal Information that we have collected.
The categories of sources from which we collected Personal
Information.
The business or commercial purpose for collecting, selling or
sharing Personal Information.
The categories of Personal Information that we sold or
disclosed for a business purpose.
The categories of third parties with whom we share personal
information.
The categories of third parties to whom the Personal
Information was sold or disclosed for a business purpose.
The specific pieces of personal information we have collected
about you.
Access. You have the right to request a copy of the Personal
Information that we have collected about you.
Correction. You have the right to ask us to Correct the Personal
Information that we have collected from you if it is inaccurate.
Deletion. You have the right to ask us to delete the Personal
Information that we have collected. Note that we will comply with
such a request regardless of whether you are located in California
or elsewhere and we will complete the deletion within forty-five
days.
You may submit requests to exercise your Right To Know, Right To
Correct and Right To Deletion of information we have collected and
maintained about you described above via email
to privacy@glowing.com or at https://support.glowing.com/hc/enus/requests/new?ticket_form_id=360002386093
Nondiscrimination. You are entitled to exercise the rights described
above free from discrimination as prohibited by the privacy laws of the
state where you reside.
Notice of Right to Opt-Out of Sale/Sharing of and the “Do
Not Sell or Share My Personal Information” Link
Right to opt-out of the Sale/Sharing of your Personal
Information
.
Opt-out of sales. You have the right to opt-out of the sale of your
Personal Information. We do not sell your information (in the sense
of providing information about you to a third party that they can
then transfer on to others or use themselves outside of their
relationship with us). However, it is your right to Opt-out should
that change.
Opt-out of sharing. You have the right to opt-out of the sharing of
your Personal Information.
You may submit requests to exercise your opt-out of the Sale/Sharing of
information we have collected and maintained about you via email
to privacy@glowing.com or at https://support.glowing.com/hc/enus/requests/new?ticket_form_id=360002386093. Alternatively, you can
request to opt-out of this Sharing of your personal information here: Your
Privacy Choices, where you will find instructions on opting-out of the use
of your information for interest-based advertising.
While the Service is not directed to children under 16 years of age, we
are required to inform you that we do not have actual knowledge that we
sell or share the personal information of consumers under 16 years of
age.
Opt-Out Preference Signals
We will process any opt-out preference signal that meets the CCPA’s
requirements as a valid request to opt-out of sale/sharing. We process
opt-out preference signals in a frictionless manner as described in the
regulations adopted pursuant to the CCPA. You may elect to use an optout preference signal for us to process in a frictionless manner through
your device and / or browser’s settings. You may also choose to opt out
through any of the other methods detailed in the previous paragraph.
Notice of Right to Limit the Use of My Sensitive Personal
Information
Limit use of your Sensitive Personal Information. You have the right
under the CCPA to request that we limit use and disclosure of sensitive
personal information (as defined in the CCPA) to certain activities
specified in California Civil Code Section 1798.121. You may exercise
your Right To Limit processing of Sensitive Personal Information we
have collected and maintained about you by submitting your request via
email to privacy@glowing.com or at https://support.glowing.com/hc/enus/requests/new?ticket_form_id=360002386093.
Deidentified data. We do not to attempt to reidentify deidentified
information that we derive from personal information, except that we
may do so to test whether our deidentification processes comply with
applicable law.
Your California privacy rights under California’s Shine the Light
law. Under California’s Shine the Light law (California Civil Code Section
1798.83), California residents may ask companies with whom they have
formed a business relationship primarily for personal, family or
household purposes to provide the names of third parties to which they
have disclosed certain personal information (as defined under the Shine
the Light law) during the preceding calendar year for their own direct
marketing purposes and the categories of personal information
disclosed. You may send us requests for this information
to privacy@glowing.com. In your request, you must include the statement
“Shine the Light Request,” and provide your first and last name and
mailing address and certify that you are a California resident. We
reserve the right to require additional information to confirm your
identity and California residency. Please note that we will not accept
requests via telephone, mail, or facsimile, and we are not responsible for
notices that are not labeled or sent properly, or that do not have
complete information.
Verifying Your Requests
We cannot process your request if you do not provide us with sufficient
detail to allow us to understand and respond to it. To verify your
requests, we may require authentication that is reasonable in light of the
nature of the personal information requested.
We do not require you to verify your identity to make a request to optout of sale/sharing or to make a request to limit where that can be
accomplished without verification.
We will need to verify your identity to process your information, access,
correction and deletion requests and reserve the right to confirm your
California residency. Depending on the nature, type, and sensitivity of
the personal information, we may require additional information from
you to match the information we already have about you, authentication
into your Glow account if you have one, government identification, or a
declaration under penalty of perjury.
We will let you know if we need more information from you to verify your
request. Please reply to our requests promptly. If we cannot verify your
request, we will let you know.
Information for Authorized Agents
You can authorize an agent to exercise your California privacy rights on
your behalf. To submit a request to us as Authorized Agent, please email
us at privacy@glowing.com. Your authorized agent may make a request
on your behalf upon our verification of the agent’s identity and our
receipt of a copy of proof that the consumer gave the agent signed
permission to submit the request or proof that you have provided the
authorized agent with power of attorney pursuant to Probate Code
sections 4121 to 4130.
Notice to Users from States other than California.
As noted above, we generally apply the opt out and other provisions of
this privacy policy to all users, regardless of whether they are residents
of California or otherwise. Those provisions are intended to comply not
only with the requirements of California law, but also with the
requirements of recently enacted Connecticut, Colorado, Utah and
Virginia law regardless of whether they are currently effective. We will
interpret our promises above broadly so that opting out of the use of
Sensitive Personal Information will also implement an opting out of
profiling under Virginia law, and the term “sharing” will include
“processing for targeted advertising” as used in Virginia law. In addition,
we will respond to any requests to appeal our privacy decisions that
comply with Virginia law in accordance with our obligations thereunder.
Notice to European users
The information provided in this “Notice to European users” section
applies only to individuals in the European Economic Area (“EEA”),
United Kingdom (“UK”) and Switzerland, which we refer to in this notice
collectively as “Europe”.
Personal information. References to “personal information” in this
Privacy Policy are equivalent to “personal data” governed by European
data protection legislation.
Controller. Glow is the controller of your personal information covered
by this Privacy Policy for purposes of European data protection
legislation (including, the EU GDPR and the so-called ‘UK GDPR’ (as and
where applicable, the “GDPR”)). See the ‘How to contact us’ section
above for our contact details.
Data Protection Officer. We have appointed a “Data Protection Officer”,
this is a person who is responsible for independently overseeing and
advising us in relation to our compliance with the GDPR (including
compliance with the practices described in this Privacy Policy). If you
want to contact our Data Protection Officer directly, you can
email: GlowDataProtectionOfficer@glowing.com.
Representatives. We have appointed the following representatives in
the EEA/UK as required by the GDPR – you can also contact them
directly should you wish:
Our representative in the EEA. Our EEA representative appointed under
the EU GDPR is VeraSafe Ireland Ltd, North Point Business Park, New
Mallow Road, Cork T23AT2P, Ireland.
You can contact them by using this form.
Our representative in the UK. Our UK representative appointed under the
UK GDPR is VeraSafe United Kingdom Ltd., 37 Albert Embankment,
London SE1 7TL, United Kingdom.
You can contact them by using this form.
Legal bases for processing. We use your personal information only as
permitted by law. Our legal bases for processing the personal
information described in this Privacy Policy are described in the table
below.
Processing purpose
Details regarding each processing
purpose listed below are provided in
the section above titled “How we use
your personal information”.
Legal basis
To operate our services
Processing is necessary to perform the contract governing our provision
of our services or to take steps that you request prior to signing up for the
services. If we have not entered into a contract with you, we process your
personal information based on our legitimate interest in providing the
services you access and request.
For research and development
For marketing and advertising
For compliance and protection
These activities constitute our legitimate interests. We do not use your
personal information for these activities where our interests are
overridden by the impact on you (unless we have your consent or are
otherwise required or permitted to by law).
To comply with law Processing is necessary to comply with our legal obligations.
With your consent
Processing is based on your consent. Where we rely on your consent you
have the right to withdraw it any time in the manner indicated when you
consent or in the services.
Further uses
The original legal basis relied upon, if the relevant further use is
compatible with the initial purpose for which the personal information was
collected.
Processing is based on your consent, if the relevant further use is not
compatible with the initial purpose for which the personal information was
collected.
Use for new purposes. We may use your personal information for
reasons not described in this Privacy Policy where permitted by law and
the reason is compatible with the purpose for which we collected it. If
we need to use your personal information for an unrelated purpose, we
will notify you and explain the applicable legal basis.
Sensitive personal information. Where the collection of your sensitive
personal information is required to operate the Service, we obtain your
explicit consent to collect such information about you. Sensitive
information includes information related to racial or ethnic origin,
political opinions, religion or other beliefs, health, biometrics or genetic
characteristics, criminal background or trade union membership. You
are free to make sensitive information public on the Community Forum
(such as your political opinions and religious beliefs) but remember that
this information is visible to other users.
Automated Decision-Making and Profiling. We are not making
automated decisions about you. We may use profiling in regard to your
personal information required to operate some of our services, for
example, to the extent needed to predict health-related effects that you
may experience from one month to the other. You can object to such
profiling by contacting us at support@glowing.com.
Your rights. European data protection laws give you certain rights
regarding your personal information. If you are located in Europe, you
may ask us to take the following actions in relation to your personal
information that we hold:
Access. Provide you with information about our processing of your
personal information and give you access to your personal
information.
Correct. Update or correct inaccuracies in your personal
information.
Delete. Delete your personal information where there is no lawful
reason for us continuing to store or process it, where you have
successfully exercised your right to object to processing (see
below), where we may have processed your information unlawfully
or where we are required to erase your personal information to
comply with local law. Note, however, that we may not always be
able to comply with your request of erasure for specific legal
reasons that will be described to you, if applicable, at the time of
your request.
Portability. Port a machine-readable copy of your personal
information to you or a third party of your choice, in certain
circumstances. Note that this right only applies to automated
information for which you initially provided consent for us to use or
where we used the information to perform a contract with you.
Restrict. Restrict the processing of your personal information, if, (i)
you want us to establish the personal information’s accuracy; (ii)
where our use of the personal information is unlawful but you do
not want us to erase it; (iii) where you need us to hold the personal
information even if we no longer require it as you need it to
establish, exercise or defend legal claims; or (iv) you have objected
to our use of your personal information but we need to verify
whether we have overriding legitimate grounds to use it.
Object. Object to our processing of your personal information
where we are relying on legitimate interests (or those of a third
party) and there is something about your particular situation that
makes you want to object to processing on this ground as you feel
it impacts on your fundamental rights and freedom – you also have
the right to object where we are processing your personal
information for direct marketing purposes.
Withdraw Consent. When we use your personal information based
on your consent, you have the right to withdraw that consent at any
time. This will not affect the lawfulness of any processing carried
out before you withdraw your consent.
Exercising These Rights. You may submit these requests by email
to privacy@glowing.com or at https://support.glowing.com/hc/enus/requests/new?ticket_form_id=360002386093. We may request specific
information from you to help us confirm your identity and process your
request. Applicable law may require or permit us to decline your request.
If we decline your request, we will tell you why, subject to legal
restrictions.
Your Right to Lodge a Complaint with your Supervisory Authority. In
addition to your rights outlined above, if you are not satisfied with our
response to a request you make, or how we process your personal
information, you can make a complaint to the data protection regulator in
your habitual place of residence.
For users in the European Economic Area – the contact information
for the data protection regulator in your place of residence can be
found here: https://edpb.europa.eu/about-edpb/board/members_en
For users in the UK – the contact information for the UK data
protection regulator is below:
The Information Commissioner’s Office
Water Lane, Wycliffe House
Wilmslow – Cheshire SK9 5AF
Tel. +44 303 123 1113
Website: https://ico.org.uk/make-a-complaint/
Cross-border data transfer. After collecting personal information
directly from you, we further transfer your personal information to some
recipients which may be located in countries in respect of which either
the European Commission and/or UK Government (as and where
applicable) has issued adequacy decisions, in which case, the
recipient’s country is recognized as providing an adequate level of data
protection under EEA/UK data protection laws (as applicable) and the
transfer is therefore permitted under Article 45 of the GDPR.
Some recipients of your personal data may be located in countries
outside the EEA and/or the UK for which the European Commission or
UK Government (as and where applicable) has not issued adequacy
decisions in respect of the level of data protection in such countries
(“Restricted Countries”). For example, the United States is a Restricted
Country. Where we transfer your personal information to a recipient in a
Restricted Country, we will either:
enter into appropriate data transfer agreements based on so-called
Standard Contractual Clauses approved from time-to-time under
GDPR Art. 46 by the European Commission, the UK Information
Commissioner’s Office or UK Government (as and where
applicable); or
rely on other appropriate means permitted by the EU GDPR/UK
GDPR, which establish that such recipients will provide an adequate
level of data protection and that appropriate technical and
organizational security measures are in place to protect personal
information against accidental or unlawful destruction, loss or
alteration, unauthorized disclosure or access, and against all other
unlawful forms of processing.
You may ask for a copy of such appropriate data transfer agreements by
contacting us using the contact details above.

OVIA
Introduction and scope
This Ovia Health by Labcorp Apps Privacy Policy (“Policy”) describes how Ovuline, Inc., doing business as Ovia Health by Labcorp (“Ovia”) collects, uses and shares personal data collected through the Ovia apps, health coaching, surveys, and related social media and marketing activities (the “Services”). Ovia Health by Labcorp is a subsidiary of Labcorp, a global life-sciences leader.

Some parts of this Policy only apply to Ovia’s free consumer version of the Services, while others only apply to the enhanced paid versions provided as a benefit by employers, health plans and health care providers. In this Policy, we refer to these different versions as the “Consumer” and “Ovia+” versions of the Services. To view the full version of this Policy, click “Full Privacy Policy” above; the “Notice of Collection” is a shorter version required for California law.

This Policy does not apply to personal data collected outside the scope of the Services. For Ovia’s non-app Privacy Policy, which covers personal data collected by Ovia from business contacts or through our corporate website, please see our Non-App Privacy Policy.

“Personal data” means information about you that identifies you, like a name, telephone number or other bit of information that is used to tell us who you are. Personal data includes “direct identifiers” such as your email address and also “indirect identifiers” that could be used to identify you such as the IP address and the Advertising ID of your mobile device.

Personal Data We Collect
We collect the following categories of personal data in connection with our Services:

Category	Examples of Data We Collect In this Category
Identifiers	Name, email address, street address, postal address, mobile phone number
Device identifiers such as IP address, AdID, IDFA
For Ovia+ members, employer ID, employee ID
General personal information including health information	Date of birth, date of last period, due date, and other fertility, pregnancy, health, sex life and life circumstances information you input into the apps or discuss as part of health coaching services
In the Parenting app, health and milestone information for your child
For Ovia+ members, health insurance information
Legally protected classifications such as race, gender, disability or pregnancy status	Race, gender, gender identity, age, ethnic group, nationality, sexual orientation, pregnancy status, disability, medical condition
Biometric information	Sleep, health and exercise data that you sync from a wearable device, Apple Health or Google Health Connect to your Ovia account. Ovia does not collect biometric identifiers such as fingerprints or voiceprints.
Internet and app activity information	App usage, browsing history, email opens and views
Device type, operating system, other device parameters
Geolocation	Approximate location by country, state, city, zipcode and regional area
Audio and visual information	Photos and videos that you upload to your Ovia account
Professional and employment related	Employment status, name of employer (for Ovia+ membership)
Inferences	Pregnancy trimester, fertile window, health issues that may be relevant to you
Sensitive information	racial or ethnic origin, health information, sex life and sexual orientation information
Where Do We Get the Information We Collect?
Categories of Sources	Examples of Our Use of These Sources
From direct input into our apps and Services	We collect the data you input into Ovia apps and Services and store it in our cloud computing environment
From wearable devices, Apple Health and Google Health Connect	If you sync a device, Apple Health or Google Health Connect with Ovia, we collect the data you choose to share
Ovia’s use of information received from Google APIs will adhere to Google API Services User Data Policy, including the Limited Use requirements.
From our coaching services and communications	We collect your communications with our care advocates, health coaches and in our Community feature
From our Ovia+ customers – employers, employer health plans, health insurers, providers	To verify your eligibility for Ovia+ services, we receive identity information (such as name, date of birth, employee ID numbers) from your organization
From your mobile device or computer and through tracking technologies	We automatically collect from your device information such as IP address and technical identifiers
We also use cookies, tags, pixels and other tracking technologies to collect information about your interaction with content and the Services generally
From surveys	We collect data you submit to us through surveys
From friends referrals and lists purchases	We may receive email addresses and contact information from referrals, co-promotions and list purchases
Purpose of Collection and Use of Personal Data
We use your personal data to:

Provide the Services to you
Understand how you use the Services, including what content and ads you view
Personalize the Services by showing you content relevant to your health, interests and fertility, pregnancy and parenting journey – for example, if you provide us with personal data indicating you have a certain health condition, we may provide you with editorial content relevant to that condition
Send you personalized emails showing relevant data points derived from the personal data you input to our Services, unless you opt-out of such communications in the Settings page of the app. Despite precautions, email communications may be intercepted; you should opt-out if you do not wish to accept this risk.
Send you marketing communications for Ovia and its affiliates, subject to your opt-in consent when required by law
Provide support and troubleshooting
Provide you with health coaching if you are an Ovia+ member
Send you email communications about the Services
Solicit your participation in surveys and run surveys
Provide security for the Services and obtain analytics about app performance
Market, develop and improve Ovia’s and its affiliates’ products and services
Conduct clinical and scientific research, subject to your informed consent where required by law
Create deidentified data and aggregated data and statistics, as described further here
Comply with law, for security management and investigation, in connection with litigation, or to protect the rights or property of Ovia or third parties
Lawful Processing. Our processing of your personal data is based on one or more of the following:

The consent you provide to us at the point of collection of your personal information;
The performance of the contract we have with you;
The compliance of a legal obligation to which we are subject;
The performance of scientific research, preparation of statistics or public health activities;
The legitimate interests of Ovia, you or a third party, where not overridden by your interests, fundamental rights or freedoms. Ovia’s legitimate interests include the lawful conduct of its business.
The table below describes the purposes for our use and collection by category.

Category	Purpose of Collection and Use
Identifiers	All purposes listed under “Purpose of Collection and Use of Personal Data” above (“Comprehensive Use”), other than creation of deidentified data
General personal information including health information	Comprehensive Use, other than uses not permitted by law.
Legally protected classifications such as race, gender, disability or pregnancy status	Comprehensive Use, other than uses not permitted by law
Biometric information	Comprehensive Use
Internet and app activity information	Comprehensive Use
Geolocation	Comprehensive Use
Audio and visual information	Store and display the photos and videos you upload to your Ovia account
Professional and employment related	To provide you with Ovia+ services
Inferences	Comprehensive Use, other than uses not permitted by law. Our primary use of inferences is to provide you with content relevant to your health.
Sensitive information	Comprehensive Use, other than uses not permitted by law.
When We Share Personal Information, What Categories of Recipients Do We Share With?
Categories of Recipients	Examples of Recipients We Share With
Service Providers and Contractors	Ovia’s data is processed and stored by service providers and contractors working on Ovia’s behalf, including our cloud services provider Amazon Web Services, Helpshift (support services platform), Salesforce.com (coaching platform), Alchemer (survey platform) and Zoom Video Communications (coaching communications).
Ovia+ Customers and their Business Associates and Health Benefit Providers	If you are an Ovia+ user, we may share data with your health insurer, health plan, employer, or their business associates and benefits management providers, as described below under the heading “Ovia+ Data Sharing”, provided that we share information with your employer only for specific uses and only if you expressly consent.
From your other devices	If you opt-in to share your Ovia data with Apple Health, Google Health Connect or your other devices, we share the information you select to share.
From surveys	We collect data you submit to us through surveys
People You Invite	The Ovia apps may allow you to invite others, such as your partner, to share your Ovia journey. If you invite someone, they will be able to see all of your personal data in the Ovia apps. The people you invite are also able to add others to your account. If you add personal data or other content to an Ovia account, everyone who is following that Ovia account will see it.
You and Your Requested Followers	If you enroll in Ovia, Ovia may send you regular email updates relevant to your Ovia journey. These emails are subject to opt-in consent where required by law. If you include a profile image or name for yourself or a child in your care, this profile image and name will be shared in emails to you and everyone who has been invited to follow your account. The name and image will be visible even before the invitation is accepted. If you do not want the image or name to be shared, you should not enter a profile picture or a profile name.
Affiliates and Successors	We may share data with our parent company Labcorp and with companies under common control, and with any successors in the event of merger, acquisition, asset sale, or similar transaction.
Government Authorities and Recipients of Compelled Disclosures	Ovia may provide personal data to courts, law enforcement, and governmental authorities and other third parties if required by law, subpoena, directive from a regulatory authority or as otherwise necessary to comply with legal requirements or to protect the rights or property of Ovia or third parties.
Please also see How Does Ovia Respond to Data Requests
Ovia+ Data Sharing
If you receive the premium “Ovia+” version of Ovia through your health insurer, employer or employer health plan, your Ovia+ services include data sharing with your insurer, employer health plan, employer, or vendors working on their behalf in accordance with HIPAA and other privacy laws.

Data sharing does not occur for all Ovia+ clients. If you would like definitive information on the data sharing for your account, please contact support@oviahealth.com. Our Ovia+ data sharing policy is as follows:

If you receive Ovia as a benefit from your health insurer or health care provider, Ovia is part of your care package and we share your personal data with your health insurer or provider, or their business associates, under HIPAA, for care and benefits management.
If you receive Ovia as a benefit from your employer or your employer health plan:
we do not share your health data with your employer unless you expressly consent for a specific purpose; this may occur, for example, if your employer offers you access to an in-house care management team. If this occurs, we limit the sharing as necessary for the specific purpose to which you have given consent. To understand more about the consent we request, see Why do we ask for this?
However, we may share personal data with your employer health plan and their business associates (including your health insurer), and with employee benefits management vendors, consistent with HIPAA or other privacy laws.
When we share your data with your health insurer, nurse care managers from your health plan may also have access to your personal data and may contact you as a result for care management purposes.
If you seek to register for Ovia+ premium services provided by a health plan or employer, we may share limited identity information (such as name and date of birth) with the health plan or employer to confirm your eligibility for Ovia+ benefits.
When we share health data for care and benefits management as described in this section, we share a summary snapshot of your health data. We do not share any information you have recorded in the Ovia apps about sexual activity, any answers you have given to MyQ questions, or any submissions you make to our Community feature.
What Categories of Personal Information Do We Sell or Share for Advertising?
As of June 2025, Ovia no longer shows advertising to our Consumer users and does not sell or share any personal data for advertising. Please see the table at the end of this document for the categories of personal data sold or shared for advertising before we terminated our advertising business.

No Selling or Sharing for Advertising of Personal Data of Consumers Under 16
To its knowledge, Ovia does not sell or share any personal data of Ovia users under 16. Ovia no longer shows advertising.

Categories of Personal Information Disclosed for Business Purposes
Category	Categories of Recipients	Business Purpose for Sharing
Identifiers	Cloud computing providers, data analytics providers, vendors who provide email, support, admin, marketing, survey and scheduling systems.	For internal operations (hosting, support, admin, marketing, analytics).
General personal information including health information	Cloud computing providers, data analytics providers, vendors who provide email, support, admin, marketing, survey and scheduling systems.
Ovia+ customers and their vendors as described under the “Ovia+ Data Sharing” heading above.	For internal operations (hosting, support, admin, marketing, analytics).
To provide our digital health solutions to Ovia+ customers.
Legally protected classifications including race, gender, pregnancy status	Cloud computing providers, data analytics providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.
Ovia+ customers and their vendors as described under the “Ovia+ Data Sharing” heading above.	For internal operations (hosting, support, admin, marketing, analytics).
To provide our digital health solutions to Ovia+ customers.
Biometric information	Cloud computing providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.
If you elect to share your Ovia data with a device provider (such as Apple or Google), we share the data you elect to share.
Ovia+ customers and their vendors as described under the “Ovia+ Data Sharing” heading above.	For internal operations (hosting, support, admin, marketing, analytics) and to provide our digital health solutions to Ovia+ customers.
If you elect to share your Ovia data with a device provider (such as Apple or Google), to provide that sharing service to you.
Internet and app activity information	Cloud computing providers, data analytics providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.
Ovia+ customers and their vendors as described under the “Ovia+ Data Sharing” heading above.	For internal operations (hosting, support, admin, marketing, analytics), and to provide our digital health solutions to Ovia+ customers.
Geolocation	Cloud computing providers, data analytics providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.	For internal operations (hosting, support, admin, marketing, analytics).
Audio and visual information	Cloud computing providers.	For internal operations (hosting and support).
Professional and employment related	Cloud computing providers, data analytics providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.	For internal operations (hosting, support, admin, marketing, analytics).
Inferences	Cloud computing providers, data analytics providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.
Ovia+ customers and their vendors as described under the “Ovia+ Data Sharing” heading above.
For internal operations (hosting, support, admin, marketing, analytics), and to provide our digital health solutions to Ovia+ customers.
Sensitive information	Cloud computing providers, data analytics providers, and vendors who provide email, support, admin, marketing, survey and scheduling systems.
Ovia+ customers and their vendors as described under the “Ovia+ Data Sharing” heading above.	For internal operations (hosting, support, admin, marketing, analytics).
To provide our digital health solutions to Ovia+ customers.
Prior to the termination of our advertising business in June 2025, we shared identifiers, internet and app activity information and inferred purchase interests with our ad sales platform, advertising networks, advertising platforms or advertising technology providers to sell, administer, serve and purchase ads.


Ovia may also share personal data for business purposes in all of the above categories, as described in the table “When We Share Personal Information, What Categories of Recipients Do We Share With?”, with the following categories listed in that table: People You Invite, You and Your Requested Followers, Affiliates and Successors, and Government Authorities and Recipients of Compelled Disclosures.

Third Parties Receiving Personal Information for Their Own Business Purposes
Ovia discloses personal data to processors who act on Ovia’s behalf (our principal processors are listed on our Subprocessors Page). Our analytics vendor Appsflyer provides its services to Ovia as a processor, but may act as a controller when using personal data for its internal security, error correction and compliance purposes.

Data Security
Ovia protects personal data with security measures that are consistent with industry standards, including background checks on all employees and data encryption in transit and at rest. Ovia’s Ovia+ product has achieved certification to the HITRUST Common Security Framework. Our principal database is hosted by Amazon Web Services, which maintains multiple security certifications. We will notify you of security incidents as required by law, and you agree that, when permitted by law, such notices may be sent by email to the email address associated with your Ovia account.

Data Retention
If you are a Consumer user, we store your data (all categories) for the period that your account is active and then for 7 years after that. After this period, we automatically delete your data. 

If you are an Ovia+ user, we store your data (all categories) during the period that you are receiving Ovia+ benefits. Ovia is generally required to delete your data after your Ovia+ benefits end. We will notify you before your data is deleted and, where possible, offer you the opportunity to convert your account to a Consumer account and retain your data.

While these are our standard retention periods, you can delete your data at any time as described in the next section.

What Are Your Choices?
Within the Ovia Apps

You can use self-service controls within the Ovia apps to exercise your data subject rights to:

Correct your data:
Go to the “More” page of your Ovia app to the “Account” section to modify your profile and health information
Opt-out of marketing emails and push-notifications
Go to the “More” page of your Ovia app, then choose “Settings”, to edit email subscriptions and opt out of email and push notifications
You can also opt out of marketing emails by using the unsubscribe link in the emails
Delete your data and account, subject to certain exceptions
Go to “More” then “Settings” and choose “reset or delete my account”, and then “delete my account”
Obtain a copy of your data
Go to “More” then “Settings” and then “export my data”
Obtain a summary statement of Ovia’s data processing
Go to “More” then “Settings” and choose “how is my data used?”
Withdraw your consent to Ovia’s data processing by deleting your data
Go to “More” then “Settings” and choose “reset or delete my account”, and then “delete my account”
For non-US users, manage your cookies
Go to “More”, “Settings”, then “Manage My Privacy Settings”
Opting Out Through Browser-Based Global Privacy Controls

Ovia does not receive a “do not sell” Global Privacy Control (GPC) signal when you are using Ovia’s mobile applications or viewing content through in-app webviews. Ovia respects “do not sell” GPC signals that we receive on the Ovia Health corporate website at www.oviahealth.com, which is governed by Ovia’s Non-App Privacy Policy.

Contacting Our Helpdesk, and Use of Authorized Agents

You may email Ovia at support@oviahealth.com to exercise any of the rights listed above and any other data subject rights provided by law. Any authorized agents seeking to exercise data subject rights on behalf of any Ovia users should contact support@oviahealth.com with their request. Ovia may require you to verify your identity by entering your username and password in order to exercise data subject rights.

You have the right not to be discriminated against for exercising your privacy rights. Contact our helpdesk if you are concerned that this has happened to you.

Appeal Rights

If your request to exercise any of your rights is refused, you may send your notice of appeal by email to legal@oviahealth.com, for review by Ovia’s Legal Department. We will resolve your appeal within 30 days of the date of receipt of your email.

Exceptions to Deletion

Even if you exercise your rights described above, Ovia may retain personal data to maintain proper business records, to comply with and as permitted by law, for security management and investigation, in connection with litigation, or to protect the rights or property of Ovia or third parties. Please see also How Does Ovia Respond to Data Requests.

Other Relevant Information

If you opt-out of marketing emails and push notifications, you will still receive account management notices. To stop all emails and push notifications, you must delete your account and data. If we delete your data, we will not delete the posts or comments you have shared publicly on Ovia’s social media, community or chat features. If you have consented to participate in a research study and subsequently request deletion of your data, we may delay deletion until completion of the study. Even if you exercise your rights described above, Ovia may retain personal data to maintain proper business records, to comply with and as permitted by law, for security management and investigation, in connection with litigation, or to protect the rights or property of Ovia or third parties. Please see also How Does Ovia Respond to Data Requests.

How to Contact Ovia with Comments or Complaints?
To contact Ovia to exercise your privacy choices, please see “What Are Your Choices?” above.

Ovia has designated a Data Protection Officer. To contact our Data Protection Officer or for questions or complaints about Ovia’s processing of personal data, contact us at:

Data Protection Officer
Ovuline, Inc., dba Ovia Health by Labcorp
3400 Computer Drive
Westborough, MA 01581
legal@oviahealth.com

Data subjects located in the EEA or UK may contact the Data Protection Officer at the address above or Ovia’s EU and UK representative at dpo@labcorp.com.

You may also have the legal right to lodge a complaint about Ovia’s data processing with your local consumer protection or data protection authority.  If you are a resident of Washington state in the US, the Washington Attorney-General’s complaint website is here.

Additional Information
Third Party Websites or Apps: Some links within the Services may interface with or take you to websites or apps that are operated by other companies. Ovia is not responsible for the privacy practices of others. You should review the privacy policies of those sites and apps.

US Location: The data we collect is transferred to servers located in the US of our cloud computing provider, Amazon Web Services (AWS); some personal data may be transferred to other US-based vendors who provide services to Ovia, including the principal vendors listed here. If you are resident outside the US, your data may as a result become subject to US jurisdiction which may provide you with weaker data protection safeguards and rights than you would enjoy in your home jurisdiction. By accepting this Privacy Policy, using the Services or providing us with your personal data you acknowledge and consent to your personal data being transferred and/or processed as described in this Policy.

Children: The Services are not available to children under 13 or who otherwise require parental consent under applicable law to use the Services or provide personal information to Ovia. Ovia does not collect personal data from children under 13. Parents and guardians may include personal data about their baby or child in their Ovia account; the parent or guardian is responsible for ensuring they have the legal right to do so.

Deidentified Data and Aggregated Data: Ovia may use personal data to create deidentified data for research and development purposes. Deidentified data is not personal data as it is no longer linked or linkable to you. If we create a deidentified dataset we maintain it as such and will not re-identify it. We may provide deidentified data to our research partners, such as universities and medical research institutions for research, and to other businesses who have engaged us to provide research services on deidentified or aggregated data. Ovia may disclose or sell deidentified data derived from patient information (as defined by the California Consumer Privacy Act); if so, such patient information is deidentified in accordance with HIPAA safe harbor or expert determination deidentification requirements. We may use personal data to create aggregated analytic data and statistics, which we may use for Ovia’s internal purposes or share with third parties. Ovia may receive compensation for sharing deidentified or aggregate data.


Social Media: Some Ovia content may appear on Ovia’s social media channels. Ovia does not collect personal data through those channels, and the respective privacy policies of the social media provider will apply to your usage of those channels.

Sale or Sharing of Personal Information Before the Termination of Ovia’s Advertising Business
Before the termination of Ovia’s advertising business in June 2025, within the last 12 months Ovia sold or shared personal data for advertising as described in the table below.

Category of Personal Information	Categories of Recipients	Purpose of Sale or Ad Sharing
Identifiers	If you separately opted-in to share data as part of a giveaway or promotion, we shared the data you agreed to share, which may have included name, email address, and physical address, with the advertisers and sponsors of that promotion.

With advertising networks, advertising platforms,  advertising technology providers and advertisers, we shared online identifiers and IP addresses.
For marketing and promotion.

To sell, administer, serve and purchase ads.
General personal information including health information	If you separately opted-in to share data as part of a giveaway or promotion, we shared the data you agreed to share, which may have included name, email address, physical address and month/year due, with the advertisers and sponsors of that promotion.	For marketing and promotion.

To sell, administer, serve and purchase ads.
Legally protected classifications such as race, gender, disability or pregnancy status	If you separately opted-in to share as part of a giveaway or promotion, we shared the data you agreed to share, which may have included include month/year due, with the advertisers and sponsors of that promotion.	For marketing and promotion.

To sell, administer, serve and purchase ads.
Purchase histories or interests	If you separately opted-in to share a purchase interest as part of a giveaway or promotion, we shared that information with the relevant advertisers or sponsors.	For marketing and promotion.

To sell, administer, serve and purchase ads.
Internet and app activity information	With advertising networks, advertising platforms, analytics providers, advertising technology providers and advertisers, we shared online identifiers, IP addresses and app and ad engagement and activity information.	For marketing and promotion.

To sell, administer, serve and purchase ads.
Geolocation	Not sold or shared for advertising.	Not applicable
Professional and employment related	Not sold or shared for advertising.	Not applicable
Inferences	If you separately opted-in to share data as part of a giveaway or promotion, we shared your pregnancy month/year due with advertisers and sponsors.

Unless you separately opted in to share specific data as part of a promotion, we did not share any inferences with advertisers or sponsors.	For marketing and promotion.

To sell, administer, serve and purchase ads.
Sensitive information	If you separately opted-in to share data as part of a giveaway or promotion, we shared your pregnancy month/year due with advertisers and sponsors. For Florida residents, because of this sharing, we were required to state: “NOTICE: This website may sell your sensitive personal data.”

Unless you separately opted in to share specific data as part of a promotion, we did not share any health data you tracked in Ovia apps with advertisers or sponsors.
For marketing and promotion.

To sell, administer, serve and purchase ads.
Changes to this Policy
Ovia may modify this Policy from time to time by posting an updated version of the Policy. When we make material changes this Policy, we will notify users by email or in-app notification.

Last updated: August 26, 2025

The principal changes in this update were:

Changing Ovia’s business name to “Ovia Health by Labcorp”

PERIOD TRACKER APP
PRIVACY POLICY 
Last Updated Aug 20, 2025 

AppManage Group #1, LLC (“Company“, “we”, “our” or “us”), acting under the Google Play and Apple App Store alias SimpleInnovation, understands the importance of protecting your privacy. This Privacy Policy explains what information of yours will be collected when you download, install, register with, access, or use this mobile application (the “App”), and how such information will be used and shared. It also explains choices you have to control the collection, correction and/or deletion of such information.

This policy applies only to information we collect in our App and in e-mail, text and other electronic communications sent through or in connection with our App. This policy DOES NOT apply to information collected in other apps or websites (including third-party websites you may access through the App), or information collected by any third party. These third parties may have their own privacy policies, which we encourage you to read before providing information on or through them.

Should you not wish to have your information gathered or used as described in this policy, you may uninstall the App from the device(s) on which you have downloaded it.

Membership in self-regulatory frameworks 
We are members of the Digital Advertising Alliance (DAA) (http://www.aboutads.info/), European Digital Advertising Alliance (http://www.edaa.eu/) and Japan Interactive Advertising Association (JIAA) (http://www.jiaa.org/). Therefore, we adhere to the cross-industry Self-Regulatory Principles for Online Behavioral Advertising, the IAB Europe EU Framework for Online Behavioral Advertising, and JIAA Behavioral Targeting Advertising Guidelines. 

The information we collect, how we use it, and the limited ways in which we share it 
User Data
When you use the App, you have the option of providing us with any of the following information, which we refer to as your “User Data”:

  •  Your first name or preferred means of address;

  •  Your email address;

  •  Menstrual cycle and period dates and length;

  •  Symptoms and moods experienced day-to-day;

  •  Sexual activity;

  •  Contraceptive methods and dates;

  •  Medicines taken;

  •  Temperature measurements;

  •  Weight measurements;

  •  Personal notes, which could, depending on what was entered, contain information which could on its own or together with other information, be used to personally identify you (“Personally Identifiable Information” or “PII”).

By default, your User Data will only be stored locally on the device from which you access the App. We cannot access your User Data if it is only stored on your device. If you so choose, you may elect to have up back-up your User Data, in which case we will upload it to Google Cloud. The Data Processing and Security Terms for Google Cloud may be reviewed at https://cloud.google.com/terms/data-processing-terms.

Your User Data is encrypted when stored in the cloud, and a limited number of our employees are the only individuals who may access it. If you elect to store your User Data in the cloud, we will ask you to provide a password to prevent unauthorized access to your User Data, and your email address so that you may reset your password if you forget it. If you choose to provide one, your name or preferred means of address will only be used to give you a more personalized experience in-App, enabling the App to refer to you by that name or other means of address. Other than these limited uses, we do not use the User Data you provide, and it is only provided to facilitate your own use of the App.

Voluntary Application Feedback
You may provide us with feedback regarding the App, either via reviews and rating in the app store, or via email. App Store reviews and ratings are posted in a public forum on app stores, we and the public can see them.  We take your feedback seriously, and often implement or incorporate user feedback. Email feedback is managed by our support staff, and neither your email nor your feedback is shared with third parties. 

Analytics Data
Anonymous data, which we refer to as “Analytics Data,” regarding your use of our App is tracked and transmitted to us by our Apps themselves. Analytics Data consists of:

A device identifier enabling other issues on the same device to be located;

Crash logs, enabling application failures to be investigated; and

App interaction signals and event data, typically indicating when an application feature has been used in a certain way.

We use Analytics Data to fix and improve the App and evaluate features, including if and when users use different features, and how quickly new features are found. Analytics Data is anonymized, meaning it cannot be traced back to you. We process Analytics Data using Google Analytics, Firebase, and Microsoft App Center, but do not otherwise share it.

Advertising Data
Like many apps, our App is in part supported by advertising. Unless you opt-out, discussed more below, we may serve ads to you by transmitting to our select advertising partners a standard advertising identifier (an “Advertiser ID”) that we collect from your device. Advertising IDs are standard across the mobile advertising industry and are used to identify a particular device for advertising purposes. Advertising IDs are random identifiers that are generated by and tied to your mobile device. An example from a Google Android device looks like this: cdda802e-fb9c-46af-9846-0233d394c712. 

Advertising IDs are typically generated once per device, so your device would always be associated with the same Advertising ID. Advertising IDs don’t contain any Personal Information in and of themselves. However, because they are typically static, a device will maintain the same Advertising ID over time, it is possible for third parties to use an Advertising ID in conjunction with location data they could collect from your device or from other apps you use, and other apps known to be associated with your device’s Advertising ID, to create inferences about you. Both Apple’s iOS or Google’s Android operating system provide a mechanism for users to reset or disable their device’s Advertising ID. If you elect to disable your Advertising ID, we respect that choice and will not send your device’s Advertising ID to our advertising partners.  

Our Period Calendar applications transmit a device’s Advertising ID without adding any other Personal Information or other additional information. We believe this results in an excellent user experience with relevant and helpful advertising, while also protecting your privacy and safety.

Purchase Data
When you purchase a subscription or other in-app item from the Apple App Store or Google Play store, that transaction is processed by the relevant app store, and not by our Company. We have no access to your payment instruments and can see only the very limited view of the transaction shared with us by the app store. The limited data we receive consists of an order ID generated by the app store, price information, the date and time of the purchase, and may in some cases contain your ZIP code of the purchaser. This limited purchase data is only used by our support staff to request refunds for you when appropriate, and is not shared with any third party.

If you request a refund for a subscription or in-app purchase made through the Apple App Store, Apple may ask us to provide information about your usage of the service (for example, duration of access, frequency of use, or amount of content consumed). This information is shared with Apple only for the purpose of processing refund requests and in accordance with Apple’s policies. By using our app, you agree that we may share such usage information with Apple in these cases.The uses above enumerate the limited ways in which we use the information provided by or collected from you and your mobile device when you use our App. If we are required to, we may also use your Personal Information to respond to a valid and enforceable court order, law, or legal process.

If we are involved in a merger, acquisition, reorganization, restructuring, or other sale or transfer of all or any portion of our assets or business, that could involve your Personal Information and User Data being transferred to the buyer or surviving entity. We value your privacy, and we will, if allowed, use reasonable efforts to notify you when your Personal Information is transferred, by posting such notice on our website or the App, and/or by contacting you if you have provided us with an email address. In the event of a transfer of Personal Information, we will instruct the buyer, surviving entity, or other third party recipient that absent your permission to do otherwise it may only use your Personal Information covered by this Privacy Policy in accordance with this Privacy Policy, even after the transfer. However, following such transfer we cannot guarantee or enforce that any such third-party will abide by our instruction. Any new information you provide after any such transfer will likely be subject to a new policy, and you should review that policy.

Third party services we use 
As mentioned, we may provide the Advertising ID associated with your the Apple or Android mobile device to the third-party ad servers or ad networks listed below (“Advertisers”). While we do not share any other data with your Advertising ID, it is possible for Advertisers to independently collect information about your online activities over time and across different websites, apps, and other online services websites by tracking your Advertising ID elsewhere. Advertisers may use this information (including the information we provide to them) to provide interest-based (behavioral) advertising or other targeted content to your mobile device.

The App includes the use of the following services:

 Service	 Contractual partner	Services	 Privacy Policy
 Google	Google LLC, USA	• Google Analytics
• Google Analytics for Firebase
• Google Tag Manager
• Google AdMob	GA – https://policies.google.com/technologies/partner-sites
Firebase – https://firebase.google.com/support/privacy 
 Amazon	A9.com, Inc., USA and Amazon Europe Core S.a r.l., Luxembourg and Affiliates	Amazon APS	https://aps.amazon.com/aps/privacy-policy/
 Facebook	Facebook, Inc. USA and Facebook Ireland Limited	Facebook Audience Network	https://www.facebook.com/about/privacy/update/
 AppLovin	Applovin Corporation	Measurement / personalization of ads	https://www.applovin.com/privacy/ 
 Fyber	Fyber (acquired by Digital Turbine, Inc.)	Measurement / personalization of ads	https://www.digitalturbine.com/privacy-policy/
 InMobi	InMobi (f/k/a mKhoj)	Measurement / personalization of ads	https://www.inmobi.com/privacy-policy/ 
 IronSource	ironSource Ltd.	Measurement/ personalization of ads 	https://www.is.com/privacy-policy/ 
 Unity	Unity Software Inc. (d/b/a Unity Technologies)	Measurement / personalization of ads	https://unity3d.com/legal/privacy-policy/
 Vungle	Vungle, Inc.	Measurement / personalization of ads	https://vungle.com/privacy/
 Pangle	Pangle	Measurement / personalization of ads	https://www.pangleglobal.com/privacy
 AppsFlyer	AppsFlyer Ltd.	Measurement / personalization of ads	https://www.appsflyer.com/legal/privacy-policy
 RevenueCat	RevenueCat, Inc.	Measurements / purchase analytics	https://www.revenuecat.com/privacy/
We do not control all of the Advertisers’ tracking technologies or how they may be used. If you have any questions about an advertisement or other targeted content, you should consult the respective privacy policies of the Advertisers. This Company privacy policy does not apply to the Advertisers further mentioned. For information about how you can opt out of receiving targeted advertising, see Choices About Your Information below.

How we protect your information
The Company uses commercially reasonable physical, managerial, and technical safeguards to preserve the integrity and security of your data. Unfortunately, the transmission of information via the internet and mobile platforms is not completely secure. Although we do our best to protect your personal information, we cannot guarantee the security of your personal information transmitted through our App. Any transmission of personal information is at your own risk. We are not responsible for circumvention of any privacy settings or security measures we provide.

Choices about your information
We strive to provide you with choices regarding the information you provide to us. This section describes mechanisms we provide for you to control certain uses and disclosures of your information.

Advertising IDs. You may object to the transfer of your Advertising ID at any given time with immediate, future effect by adjusting the settings on your mobile device to, depending on your operating system, disable the Apple-Ad-Tracking via IFDA or to opt out of interest-based ads via the Google advertising ID. The mechanism for opting of out of interest-based ads is different for each device, so please consult the user manual for your device’s operating system for specific instructions. Additionally or alternatively, you can reset your Advertising ID at any time (and as frequently as you would like), which causes Google’s or Apple’s system to build your device’s profile for advertising purposes anew, so that advertisers cannot link your activities taking place prior to the reset to your device.

Other Tracking Technologies. Depending on your device, you may be able to adjust the settings of your device to disable or refuse app cookies and/or other tracking technologies. Please note that we do not access your device’s do-not-track settings, and we therefore do not respond to such settings. Third party advertisers, ad networks, and ad servers that display ads in our App may, however, access and respond to your device’s and browsers’ do-not-track signals; if you would like to know how a third party advertiser responds to do-not-track signals sent by your device or browser, please consult their privacy policy.

Targeted Advertising by Third Parties. We do not control third parties’ collection or use of your information to serve interest-based advertising. However, these third parties may provide you with ways to choose not to have your information collected or used in this way. In general, to find out more about how to opt out of receiving targeted ads from a particular advertiser click on the AdChoices icon or link (or similar icon or link) appearing in or near the ad.  You can also opt out of receiving targeted ads from members of certain ad networks as follows:

 If the Advertiser is a member of or advertises through:	 To Opt Out
 Digital Advertising Alliance	 Install and use the AppChoices App
 European Interactive Digital Advertising Alliance	 Opt out at http://www.youronlinechoices.eu/
 Google Ads	 Learn how to opt out at Google Ads Help - Opt Out.
You can stop all collection of information by the App by uninstalling the App. You may use the standard uninstall processes as may be available as part of your mobile device or via the App’s marketplace or network.

Accessing, correcting and updating your information; your rights regarding your information
Access, Review, and Modification of Information; Deleting Information
Users may request to access, update, change, or delete their Personal Information via the Contact page on https://www.simpleinnovation.us/contact or by email at feedback@period-tracker.com. 

We will attempt to respond to your requests within one month and free of charge. Please note that with regard to all these rights, we reserve the right to:

Verify your identity in order to process the request, or request further information for this purpose;

Refuse your request based on the exemptions set out in any applicable data protection laws; and

Charge you a reasonable administrative fee for any repetitive, manifestly unfounded, or excessive requests.

Your California Privacy Rights
As noted above, we do not sell or share any User Data. We may, however, provide Advertising IDs from your device to Advertisers. Under certain laws, including California law, the provision of Advertising IDs may constitute a sale of Person Information. As discussed above, you may at any given time with immediate, future effect by adjusting the settings on your mobile device to, depending on your operating system, disable the Apple-Ad-Tracking via IFDA or to opt out of interest-based ads via the Google advertising ID. Please see the Choices About Your Information section above for more information.

In addition, if you are a California resident, you have the right to request information from us regarding the ‎manner in which we share certain categories of your Personal Information with third parties. ‎Specifically, California law provides you the right to submit a request to us at the designated address in the Contact Us section below, or via the Contact page on https://www.simpleinnovation.us/contact or by email at feedback@period-tracker.com, to ‎request that we:‎

Disclose to you the following information covering the 12-month period prior to your request:

The categories of Personal Information we collected about you and the categories of sources from which we collected the Personal Information;

The business or commercial purpose for collecting Personal Information about you;

The categories of third parties to whom we disclosed Personal Information about you, and the categories of Personal Information disclosed;

The specific pieces of Personal Information we collected about you;

Delete the Personal Information we collected from you; and

Correct Personal Information we collected from you.

You are entitled to receive a copy of this information in a standardized format and the ‎information will not be specific to you individually. In addition, you have the right to be free from discrimination by a business for exercising these rights.

Under California law, you also have a right to know that, as described in The Information We Collect, How We Use It, And The Limited Ways In Which We Share It section above:

In the last 12-month we have collected the following categories of Personal Information: 

Personal unique identifiers, when you provide us with a name or other preferred means of address;

Personal information, when you provide us with an email address, if we receive a zip code from an app store, or if you upload personal health information such as information about your cycle or sexual activity; and

Biometric information, when you provide us with information about medicines taken, temperatures, or measurements;

In the last 12 months we have shared Personal Information for a business purpose when:

users elect to have their User Data stored in the cloud and we send such data to Google Cloud; and

we provide anonymized Analytics Data to Google Analytics; and

In the last 12 months, unless you have opted-out, as described above, we have provided your device’s Advertising ID to our Advertisers, which may be considered a “sale” or Personal Information.

Data subjects in the EU
If you are located in the EU when using our services, the following information is relevant for you.

To contact our Data Protection Officer, you may send an email to feedback@period-tracker.com with the subject ATTN: DPO. Through the use of SDKs, we allow our advertising partners in the US to collect non-PII data, which they store and use to provide us with more relevant advertising. The legal basis of the processing of this information is Art. 6 para 1 lit a) GDPR, your consent. You may withdraw your consent at any given time with future effect by following the withdrawal mechanisms described in the Privacy Policies of our partners, the Opt-Out procedures provided by the DAA, EIDAA and Google Adds described above, modifying the Settings in the App(s) you use, or by uninstalling the app. When you ask us to store a backup of your User Data with Google Cloud, the legal basis for our doing so is Art 6 para 1 lit b) GDPR, the performance of the agreement formed between you and us when you asked us to send your User Data to Google Cloud. You are not obliged to provide your information to us, neither by operation of law nor contract. If you do not provide consent to us, we will not be able to personalize your ads or measure your use of our services. You have the right to request access to and rectification or erasure of personal data and restriction of processing as well as a right to data portability and you may always lodge a complaint with a supervisory authority.

Changes to our Privacy Policy
We reserve the right to modify this Privacy Policy in our sole discretion. If we change our Privacy Policy, we will make the updated privacy policy available from within the App. Changes to this Privacy Policy are effective when they are posted. The date the privacy policy was last revised is identified at the top of the page. You are responsible for periodically visiting this privacy policy to check for any changes.

Contact us
If you have any questions or concerns about our Privacy Policy, please contact us at feedback@period-tracker.com.

AppManage Group #1, LLC : 15127 NE 24th  Street

Ste 132

Redmond, WA 98052


MAYA
Terms and Privacy Policy
TERMS OF USE

Please read the following terms of use (“Terms of Use” or “Terms”) of the application, Maya (“Application”).

For the purpose of these Terms of Use, wherever the context so requires “You” or “User” shall mean any natural or legal person who has agreed to become a registered User on the Application by providing registration data while registering on the Application. The term “We”, “Us”, “Our” shall mean Plackal Techno Systems Private Limited (“Maya” or the “Company”, which expression shall, wherever the context permits, admits or requires, be deemed to mean and include its successors in interest and permitted assigns). The Application is owned and operated by the Company. Please read the Terms carefully before logging in, or using in any manner whatsoever the Application.

You will be bound by the Terms of Use set forth herein and the Privacy Policy available here http://plackal.in/terms-and-privacy-policy/. These Terms of Use and the Privacy Policy constitute a valid and legally binding agreement between You and Us, Plackal Techno Systems Private Limited. By logging in, or using the Application, You agree to be bound by these Terms, the Privacy Policy including any additional guidelines and future modifications. If You find any of these Terms or any provisions of the Privacy Policy unacceptable, do not tender Your acceptance to use the Application or any of its features. You acknowledge that the Company is providing You with a revocable, limited, non-exclusive, and non-transferable license to use the features of the Application.

This document is an electronic record in terms of the Information Technology Act, 2000 (“IT Act”), the rules thereunder as applicable, and the provisions pertaining to electronic records in various statutes as amended by the IT Act. This electronic record is generated by a computer system and does not require any physical or digital signatures.

When You use the Application You will be subject to these Terms of Use. We may update these Terms of Use from time to time and will notify You as and when We do so. Please ensure You read our Terms of Use and any updated version when You use the Application.

Company and You may be individually referred to as a “Party” and collectively as “Parties”, as the context may require.

 

1.0       Acceptance of Terms

1.1       These Terms set forth a legally binding contract between You and Us. By using the Application, You agree to be bound by these Terms. Even if You only visit this Application or review any of the services offered by Us, You will be bound by these Terms. If You do not accept these Terms You must not use the Application.

1.2       To accept these Terms, You must be at least 18 (eighteen) years of age or such other older legal age as is required in Your jurisdiction to form a legally binding contract in Your jurisdiction. In the event that You are below 18 (eighteen) years of age or such other older legal age as is required in Your jurisdiction to form a legally binding contract, please ensure that Your guardian accepts these Terms and has read and understood the provisions of the Privacy Policy on Your behalf.

1.3        In consideration of Your use of the Application, You represent that You are of legal age to form a binding contract and are not a person barred from receiving services under any law in force in India or other applicable jurisdiction. You also agree to:

provide true, accurate, current and complete information about Yourself as prompted on the Application;
maintain and promptly update Your data to keep it true, accurate, current and complete.
1.4        If You provide any information that is untrue, inaccurate, not current or incomplete, or We have reasonable grounds to suspect that such information is untrue, inaccurate, not current or incomplete, We reserve the right to suspend or terminate Your account and refuse any and all current or future use of the Application (or any portion thereof) at any time.

1.5        You may access the Application as available for Your personal use.

1.6        You will be required to enter a valid phone number while registering on the Application. By registering Your phone number with us, You consent to be contacted by Us via phone calls, SMS notifications, and/or e-mails, in case of any subscription/service updates.

 

2.0       Services

2.1        To avail any services offered by the Company, You will have to register with the Application to create Your account. You may then update the Application with personal information relating to You.

2.2        The Company offers You a technology platform via the Application which facilitates You to update Your information to help You track Your period cycles (“Cycles”), flow duration and also help predict Your next Cycle contingent to the information update by You.

2.3        The Company does not guarantee the consistency or the stability of the Application. Further, any services provided by the Company may be subject to change at the discretion of the Company, and the Company does not require Your permission for the same.

2.7        The Application also automatically syncs the data entered by You to Your registered e-mail address.

2.8        The Application allows You to password protect it, in the event that You wish to do so.

 

3.0       Premium Services

3.1        You may use our premium services by paying an amount as specified in the Application to avail exclusive premium services. These premium services may be different for each user of the Application.

3.2        Any payments made to the Company in respect of premium services are non-refundable and there are no refunds or credits for partially used periods.

3.3        The Company may at its discretion revise the amount payable in respect of premium services, and any services that may be applicable to premium Users. The Company also does not guarantee that the exclusive services will remain exclusive only to a premium User, these services may also be provided to users who have not paid the requisite fee to upgrade their services to premium.

 

4.0       Health Disclaimer

4.1        Any information provided to You through this Application, including, but not limited to, any predictions, and/or advice should not be treated as medical advice, diagnosis or treatment. We suggest You consult a qualified Doctor for any queries or clarifications about Your Cycles or health in general.

4.2        The Company shall not be held responsible for any reason whatsoever, if You use this website Application as a method of contraception or conception. The purpose of this Application is to keep track of Your Cycles according to the dates entered by You.

4.3        PLEASE NOTE, THE COMPANY, ITS OFFICERS, AND EMPLOYEES ARE NOT QUALIFIED TO GIVE MEDICAL ADVICE OR PROGNOSIS AND WE DO NO’T GIVE ANY SUCH MEDICAL ADVICE. PLEASE CONSULT YOUR DOCTOR FOR ANY PROBLEMS.

4.4        You expressly waive and release any claim that You may have against the Company or its directors, employees, agents, contractors, affiliates and representatives at any time for any health concerns issues of any kind that You may experience as a result of Your use of the Application.

4.5        The Company does not recommend or endorse any specific tests, physicians, products, procedures, opinions, or other information that may be mentioned on the Application. Reliance on any information provided by the Company, employees, others appearing on the Application is solely at your own risk. The Application and any content on it is provided on an “AS IS” basis.

 

5.0        User Account, Password and Security

5.1         If You download the Application, You may be required to choose a password, passcode, and nick name. You are responsible for maintaining the confidentiality of Your password, passcode and account information, and are fully responsible for all activities that occur under Your password, passcode or account. If there is any compromise on Your password and/or Your passcode You can change Your password and or passcode using the ‘forgot password’ and/or ‘forgot passcode’ functionality.

 

6.0       Prohibited Conduct

6.1        You agree that You shall not use the Application in order to host, display, upload, modify, publish, transmit, update, distribute, share, store or destroy material:

in violation of any applicable law or regulation;
in a manner that will infringe the copyright, trademark, trade secret or other intellectual property or proprietary rights of others or violate the privacy, publicity or other personal rights of others;
that belongs to another person and to which the user does not have any right to;
that is grossly harmful, harassing, blasphemous, defamatory, obscene, pornographic, paedophilic, libellous, invasive of another’s privacy, threatening, abusive or hateful or racially, ethnically objectionable, disparaging, relating encouraging money laundering or gambling or otherwise unlawful in any manner whatsoever;
harm minors in any way;
deceives or misleads the addressee about the origin of such message or communicates any information which is grossly offensive or menacing in nature;
impersonate another person or entity;
contains software viruses or any other computer code, files or programs designed to interrupt, destroy or limit the functionality of the Company’s computer systems or site or the Company’s users, customer’s computer systems or site;
threatens the unity, integrity, defence, security or sovereignty of India, friendly relations with foreign states or of public order or causes incitement to the commission of any cognizable offence or prevents investigation of any offence or insulting any other nation.
6.2        If You become aware of misuse of the Application by any person, please contact email@plackal.in

 

7.0        Termination or Suspension of Account

7.1        You agree that the Company may at any time and for any reason, terminate Your access to the Application, or restrict or suspend Your access to all or any part of the Application at any time, for any or no reason, with or without prior notice, and without liability. If there is a suspicion of untoward or illegal activity, we may suspend Your account immediately.

 

8.0        Preservation/Disclosure

8.1        You acknowledge, consent and agree that the Company may access, preserve and disclose Your account information if required to do so by law or in a good faith belief that such access, preservation or disclosure is reasonably necessary to:

comply with legal process nationally or internationally;
enforce this Agreement;
respond to claims that any Content violates the rights of third parties;
protect the rights, property or personal safety of the Company, its users and the public; or
pursuant to the terms of the Privacy Policy (http://plackal.in/terms-and-privacy-policy/).
we may use Your information to reach You for marketing or promotional purposes through any channel.
 

9.0         Security Components

9.1         You understand that the Application and software embodied within the Application may include security components that permit digital materials to be protected, and that use of these materials is subject to usage rules set by the Company. You may not attempt to override, disable, circumvent or otherwise interfere with any such security components and usage rules embedded into the Application.

 

10.0      Proprietary Rights

10.1      All materials on the Application, including, without limitation, names, logos, trademarks, images, text, columns, graphics, graphs, illustrations, artwork, software and other elements (collectively, “Material”) are protected by copyrights, trademarks and/or other intellectual property rights owned and controlled by the Company. You acknowledge and agree that all Material on the Application is made available for limited, non-commercial, personal use only. Except as specifically provided herein or elsewhere in the Application, no Material may be copied, reproduced, republished, sold, downloaded, posted, transmitted, or distributed in any way, or otherwise used for any purpose, by any person or entity, without the Company’s prior express written permission. You may not add, delete, distort, or otherwise modify the Material. Any unauthorized attempt to modify any Material, to defeat or circumvent any security features, or to utilize the Application or any part of the Material for any purpose other than its intended purposes is strictly prohibited.

 

11.0       Maya and Links to Third Parties

11.1       Our Application may contain links to other apps or websites owned by third parties (i.e. advertisers, affiliate partners, strategic partners, or others). We are not responsible for examining or evaluating, and we do not warrant the products or offerings of, any of these businesses or individuals, or the accuracy of the content of their applications or websites. The Company does not assume any responsibility or liability for the actions, product, and content of any such applications or websites. Before You access or visit any third party applications or websites, You should review the applicable terms of use and prevailing policies for such applications or websites. If You decide to access any such third party platform, You do so at Your own risk.

 

12.0       International Use

12.1       Due to the global nature of the Internet, You agree to comply with all applicable local (Indian) laws and regulation rules regarding use of the Application. Specifically, You agree to comply with all applicable laws regarding the transmission of technical data exported from India or the country in which You reside.

 

13.0     Trademark, Copyright and Restriction

13.1      The Application is proprietary software developed and made available exclusively by the Company. The Company is the sole owner of the Application, and all software created to make the Application available to You. The Company provides You with a single limited license to download, use and access the Application on Your mobile telephone devices for the limited purpose of using the services. The license is specifically personal, non-transferable, and non-exclusive. All content on the Application, which is including, but not limited to, designs, text, graphics, graphs, images, information, logos, button icons, software, audio files and any other content (“Content”)  are the exclusive and sole property of the Company.

13.2      All icons and logos are trademarks of and proprietary to the Company. The unauthorized copying, modification, use or publication of these marks is strictly prohibited.

13.3      All Content is the exclusive copyright of the Company or its licensors, except the Third Party Content and link to third party apps or websites. Systematic retrieval of the Company’s Content to create or compile, directly or indirectly, a collection, compilation, database or directory (whether through robots, spiders, automatic devices or manual processes) without written permission from the Company is prohibited. In addition, use of the Content for any purpose not expressly permitted by the Company in these Terms is prohibited and may invite legal action.

13.4      All material on this site, including images, illustrations, audio clips, and video clips, are protected by copyrights, trademarks, and other intellectual property rights. Material on the Application is solely for Your personal, non-commercial use. You must not copy, reproduce, republish, upload, post, transmit or distribute such material in any way, including by email or other electronic means and whether directly or indirectly and You must not assist any other person to do so. Without the prior written consent of the Company, modification of the Content, use of the Content on any other website, Application or networked computer environment or use of the materials for any purpose other than personal, non-commercial use is a violation of the copyrights, trademarks and other proprietary rights, and is prohibited. Any use for which You receive any remuneration, whether in money or otherwise, is commercial use for the purposes of these Terms.

13.5      The Company respects the intellectual property of others. In case You feel that Your trademark or copyright has been infringed, You can write to us at email@plackal.in.

 

14.0     Terms and Termination

14.1.      These Terms of Use shall remain in full force and effect for so long as You use the Application. You may delete Your account at any time, for any reason, by following the instructions on the Application. The Company however does not offer any refunds.

14.2       The Company reserves the right to terminate the services or the Application without prior notice. Your account or Your access to the Application maybe terminated immediately, with or without notice to You, and without liability to You, if the Company believes that You have breached any of these Terms, the Privacy Policy, or any false or misleading information, or interfered with use of the Application by others.

14.3       The Company reserves the right to cancel delete or deactivate Your Account, if it believes the same has been compromised, or is being used fraudulently, at its own discretion.

 

15.0       Disclaimer of Warranties and Liability

15.1       All Material on this Application, (including but not limited to software) and services, included on or otherwise made available to You through this Application are provided on “AS IS” and “AS AVAILABLE” basis without any representation or warranties, express or implied except otherwise specified in writing. Without prejudice to the forgoing paragraph, the Company does not warrant that:

The Application will be constantly available, or available at all; or
The information on the Application is complete, true, accurate or non-
15.2       The Company will not be liable to You in any way or in relation to the Material, or use of, or otherwise in connection with the Application. The Company does not warrant that the Application, information, content, materials, product (including software) or services included on or otherwise made available to You through the Application are free of viruses or other harmful components.

15.3       Nothing on the Application constitutes, or is meant to constitute, advice of any kind.

15.4       SUBJECT TO APPLICABLE LAWS, IN NO EVENT WILL THE COMPANY OR ITS EMPLOYEES’, OR ITS AGENTS’, PARTNERS, AND CONTRACTORS’, AGGREGATE LIABILITY ARISING FROM OR RELATED TO THE AFORESAID SERVICES SHALL EXCEED THE PAYMENTS ACTUALLY RECEIVED AND RETAINED BY THE COMPANY FROM YOU, FOR ANY AND ALL CAUSES OF ACTION BROUGHT BY YOU OR YOUR AGENTS.

 

16.0       Exclusions and Limitations

16.1      Those who access or use the Application from other jurisdictions do so at their own volition and are responsible for compliance with the local law. Some jurisdictions do not allow the exclusion of certain warranties or the limitation or exclusion of liability for incidental or consequential damages. Accordingly, in certain jurisdictions, some of the above limitations of liability may not apply to You; all other provisions of these Terms remain in full force and effect.

 

17.0      Indemnity

17.1      You agree to defend, indemnify and hold harmless the Company, its subsidiaries, affiliates, subcontractors, officers, directors, employees, consultants, representatives and agents, from and against any and all claims, damages, obligations, losses, liabilities, costs or expenses (including but not limited to attorneys’ fees and costs) arising from:

Your use of and access to the Application;
Your violation of any Terms and the Privacy Policy contained herein;
Your violation of any third party right, including without limitation any copyright, property, or privacy right.
 

17.0     Additional Terms

18.1      We may also require You to follow additional rules, guidelines or other conditions in order to participate in certain promotions or activities available through the Application, to obtain certain premium Content through the Application, or for other reasons. These additional terms are part of this Agreement, and You agree to comply with them when You participate in those promotions, or otherwise engage in activities governed by such additional terms.

18.2      We reserve the right at any time to modify, edit, delete, suspend or discontinue, temporarily or permanently the service or any of the Application (or any portion thereof) with or without notice. You agree that we will not be liable to You or to any third party for any such modification, editing, deletion, suspension or discontinuance of the Application.

18.3      This Agreement and any rights and licenses granted hereunder, may not be transferred or assigned by You, but may be assigned by the Company without restriction.

18.4      This Agreement together with the Privacy Policy and any other legal notices published by the Company on the Application, shall constitute the entire agreement between You and the Company concerning the Application and governs Your use of the Application, superseding any prior agreements between You and the Company with respect to the Application.

18.5      The failure of the Company to exercise or enforce any right or provision of these Terms shall not constitute a waiver of such right or provision. If any provision of these Terms is found by a court of competent jurisdiction to be invalid, the Parties nevertheless agree that the court should endeavour to give effect to the Parties’ intentions as reflected in the provision, and the other provisions of this Agreement remain in full force and effect.

18.6      These Terms are governed by the laws of India. Any matters arising under these terms shall be subject to the exclusive jurisdiction of courts located in Bangalore.

 

19.0     Grievance Officer

19.1      In case of any grievance arising from the use of the App, please contact the Grievance Officer, the details of which are set forth below:

Grievance Officer: Name: John Paul  Contact: email@plackal.in

 

Privacy Policy

 

By reviewing our website http://maya.live/ (“Website”) or by using our services through the mobile application Maya (“App”), (collectively “Platforms”), you agree to be bound by the terms of this Privacy Policy.

By visiting our Platforms and/or by providing Your information, You consent to the collection and use of the information You disclose on our Platforms in accordance with this Privacy Policy, including but not limited to, your consent for sharing your information as per this Privacy Policy. You acknowledge and agree that even if You are not a registered User with Us, We may collect information about You, if a registered User has provided Us with Your information to facilitate services.

If we decide to change our Privacy Policy, We will post those changes on this page so that You are always aware of what information We collect, how We use it, and under what circumstances We disclose it. If You do not agree for the forgoing, please do not continue to use or access our Platforms.

For the purpose of this Privacy Policy, the term “Us”, “We”, “Maya” or the “Company” refers to Plackal Techno Systems Private Limited. The term “You” or “User” refers to the end user.

 

1.0      Collection of Personally Identifiable Information

1.1      We collect certain information about You to help us serve You better. The information collected by Us is of the following nature:

Name, e-mail address and other profile data that may have chosen to provide on the App.
Any customisations that you may have made in the App, including, but not limited to, any notes, symptoms, or moods
Any information that you enter into the App, including the length of Your menstrual cycles, and general information about Your health such Your weight, mood, temperature and/or any physical intimacy.
1.2      When using Our Website, Our server will collect the following information such as:

Your IP address
The website from which you were referred to our website (e.g. if you followed a link)
The webpages you are visiting on our website
The browser you are using and its display settings
Your operating system
The date and duration of your visit
1.3      On receiving personal information about Our Users, You no longer remain anonymous to Us. We may use this information to do internal research on our Users’ demographics, interests, and behaviour to better understand, protect and serve our Users. This information is compiled and analysed on an aggregated basis. We indicate fields that are mandatorily required to be filled and fields that are optional. The Users may decide whether or not to provide such information to Us.

cn Our Website, You can browse without telling Us who You are or revealing any personal information about Yourself. We may automatically track certain information about You based on Your behaviour on Our Website. This information may include the URL that You just came from (whether this URL is on our Platforms or not), which URL You next go to (whether this URL is on our Platforms or not), Your browser information, and Your IP address.

1.5      On Our Website, We use data collection devices such as “cookies” on certain pages to help analyse our web page flow, measure promotional effectiveness, and promote trust and safety. “Cookies” are small files placed on your hard drive that assist Us in providing Our services. We offer certain features that are only available through the use of a “cookie”. You are always free to decline our cookies if Your browser permits, although in that case You may not be able to use certain features on the Platforms. Additionally, You may encounter “cookies” or other similar devices on certain pages of the Website that are placed by third parties. We do not control the use of cookies by third parties.

 

2.0     Additional Information

When You use Our services, We may collect information about You, with Your permission, in the following general categories:

2.1      Location Information: When You use the Platforms through the telecommunication device, we collect Your location data. If You permit the Platforms to access Your location through the permission system used by Your mobile operating system, We may also collect the precise location of Your device when the App is running in the foreground or background. We may also derive Your approximate location from Your IP address.

2.2      Device Information: We may collect information about Your mobile device, including, for example, the hardware model, operating system and version, software and file names, preferred language, unique device identifier, advertising identifiers, serial number, device motion information, and mobile network information.

 

3.0     Use of Personal Information

3.1      The information collected by Us through our Platforms maybe used inter alia for the following purposes:

To provide Our services to You;
Internal record keeping;
To improve Our products and services.
3.2      We may periodically send promotional e-mails or messages on the App about special offers or other information which We think You may find interesting;

3.3      From time to time, We may use the information to customize the Website or App according to Your interests.

3.4      We may use personal information to resolve disputes that may arise with the use of Our Services, help promote a safe service to all the Users of the Platforms, measure consumer interest in our services, customize your experience, detect and protect Us against error, fraud and other criminal activity, enforce Our terms and conditions.

3.5      We identify and use Your IP address to help diagnose problems with Our server, and to administer Our Platforms. Your IP address is also used to help identify You and to gather broad demographic information.

 

4.0      Sharing of Personal Information

4.1      We share Your information with payment service providers and regulatory authorities in the event of any request from such authorities.

4.2      We may disclose Your personal information if required to do so by law or in the good faith belief that such disclosure is reasonably necessary to respond to subpoenas, court orders, or other legal process. We may disclose personal information to law enforcement offices, third party rights owners, or others in the good faith belief that such disclosure is reasonably necessary to enforce our Terms or Privacy Policy; respond to claims that an advertisement, posting or other content violates the rights of a third party; or protect the rights, property or personal safety of our Users or the general public.

4.3      We and Our affiliates will share/sell some or all of the collected information with another business entity should We (or our assets) plan to merge with, or be acquired by that business entity, or re-organization, amalgamation, restructuring of business. Should such a transaction occur, that other business entity (or the new combined entity) will be required to follow this Privacy Policy with respect to all the information collected.

4.4      We do not disclose personal information about identifiable individuals to advertisers, but We may provide them with aggregate and/or anonymised information about our Users to help advertisers reach the kind of audience they want to target. We may make use of the information We have collected from You to enable Us to comply with our advertisers’ wishes by displaying their advertisement to that target audience.

4.5      We may share Your information with our sponsors, and/or business partners. Your Information could be shared so that you may receive newsletters, offers, information about new services, and other information, if applicable. The information collected from You and other users may be analysed in different manners.

 

5.0      Information Safety

All information is saved and stored on servers, which are secured with passwords and pins to ensure no unauthorised person has access to it. Once Your information is in our possession we adhere to strict security guidelines, protecting it against unauthorized access.

 

6.0      Choice/Opt-Out

6.1      We provide all Users with the opportunity to opt-out of receiving non-essential (promotional, marketing-related) communications from Us on behalf of our partners, and from Us in general, after providing Us with personal information. If You want to remove your contact information from all lists and newsletters, please contact help@maya.live

6.2      If You choose to unsubscribe from the Application or delete any or all of your information, you may send an e-mail to help@maya.live. Please note, We may still retain some information and record of transactions as required by any law, contract or policy applicable to Us.

 

7.0      Third Party Links

We use third-party advertising companies to serve advertisements when You visit our Platforms. These companies may use information (not including your name, address, email address, or telephone number) about Your visits to this and other platforms in order to provide advertisements about services of interest to You.

 

Refund Policy

 

By reviewing our website http://maya.live/ (“Website”) or by using our services through the mobile application Maya (“App”), (collectively “Platforms”), you agree to be bound by the terms of this Refund Policy

1.0    In the event it is proved that the Practitioners have acted against any law in force in India, We shall provide You a complete refund, subject to investigation undertaken by Us.

2.0     If the cancellation is due to the abusive nature displayed by You, You shall not be eligible for any refund and the Company/Practitioner shall be entitled to take any legal action, depending upon the gravity of the matter.

3.0     In case a Practitioner is not available in the case of a paid consultation, then such consultation shall be deemed to be cancelled and You shall be entitled to a refund or a new consultation.

4.0     You are allowed a period of three (3) days to flag any consultation as inadequate, and request for a refund. No refund requests shall be considered thereafter.

5.0     You can request a refund by writing to Us at support@maya.live

6.0     On reviewing the details of your request, We will process the refund where applicable, solely at our discretion. After a refund request is processed, your money will be refunded in seven (7) working days from the day the refund has been approved by Us


MIA PERIOD TRACKER & CYCLE CALENDAR

Privacy Policy
This privacy policy ("Policy") explains how personal information is collected, used, and disclosed by our mobile application ("Mia - Period Tracker & Cycle Calendar"). By using the Mia - Period Tracker & Cycle Calendar, you agree to the terms of this Policy.

1. Information We Collect
We may collect personal information from you in various ways when you use our Mia - Period Tracker & Cycle Calendar, including information you provide directly, information that is automatically collected, and information we get from third parties.

2. How We Use Your Information
We may use the information that we collect for the following purposes: to provide, operate, maintain, improve, personalize, and promote our Mia - Period Tracker & Cycle Calendar; to communicate with you about the Mia - Period Tracker & Cycle Calendar, and to send you technical notices, updates, security alerts, and support and administrative messages.

3. Third-party Services and Advertising
We may use third-party services such as Facebook Ads, Google Ads, TikTok Ads, and Firebase to display advertisements on our Mia - Period Tracker & Cycle Calendar, to manage our advertising on other sites, apps and services, and to track and analyze use of the Mia - Period Tracker & Cycle Calendar, determine the popularity of certain content and better understand user behavior.

4. Security
We take reasonable measures, including administrative, technical, and physical safeguards, to protect your information from loss, theft, misuse, and unauthorized access, disclosure, alteration, and destruction.

5. Privacy Policy Changes
We may change this Policy from time to time. If we make changes, we will notify you by revising the date at the top of the Policy and, in some cases, we may provide you with additional notice.

6. Contact Us
If you have any questions about this Policy, please contact us at admin@neoapps.co.uk.


APPLE HEALTH 
Health App & Privacy

The Health app is designed to protect your information and enable you to choose what you share.



The Health app can consolidate data from your iPhone, iPad, Apple Vision Pro, Apple Watch and other devices, health records, and apps you use so you can have a more comprehensive view of your health information in one convenient place. You are in control over which data is stored in the Health app and which data is shared with third-party apps and people you trust.

You remain in control over which Health app features you use, such as Health Records, Cycle Tracking, Medications, Mental Health, and Sleep. Some iOS and watchOS features (such as Heart Rate and Noise notifications) may be enabled by default. You can enable or disable the features available in the Health app at any time by tapping the Browse tab or your Profile, then tapping the health category or feature that you want to enable or disable. Certain health features may use your region to determine feature availability.

When your device is locked with a passcode, Touch ID, or Face ID, all of your health and fitness data in the Health app — other than your Medical ID — is encrypted and inaccessible by default. Additionally, if you are using iOS 12 or later and turn on two-factor authentication, Apple will not be able to read your health and activity data synced to iCloud.

You can choose to use iCloud to keep your data up to date across your devices, choose to back up your data to an iTunes encrypted backup on your computer, or choose to share your data. The Health app also gives you the ability to export a copy of your Health app data available on your device. To do so, tap your profile picture in the upper-right corner, then tap Export All Health Data.

iCloud Backup and Sync

You can choose to back up your health data in iCloud where it is encrypted while in transit and at rest. iCloud sync also allows you to keep your health data up to date across all your devices. Additionally, with iCloud sync, you can use the Health app sharing features, such as sharing Health app data with other third-party apps you trust. If you have enabled iCloud, your Health app data is backed up by default. You can disable iCloud backup at any time by going to Settings > [your name] > iCloud > See all, then tapping to turn off Health.

Sharing

Share Health App Data with Third-Party Apps
You can choose to share your Health app data with third-party apps you trust. Apps must request the ability to read data from or write data to your Health app. All third-party apps must explain why they are requesting access to your Health app data. Each app is also required to have a privacy policy that describes its use of health data, so you should review these policies before providing apps with access to your health data. You have control over the data that you share with these third-party apps and can change what you share at any time. You can view at any time which third-party apps you have granted access to your Health app data and manage what data you share with and receive from these third-party apps. Some Health app data types may not be accessible to third-party apps. Learn more about how to manage the data you share with and receive from third-party apps at support.apple.com/108779.

Share Health App Data with Family and Friends
You can also choose to share your Health app data with people you trust. You can select and share certain Health app data with other Health app users in your Contacts, such as your family and friends.

You maintain control over which data is shared with other Health app users. After the person you choose to share your health data with accepts your invitation, they will be able to view a summary of the data you share in the Health app, including a subset of your historical health data and future updates relating to the data you share, unless you decide to stop sharing. They can also choose to receive alerts, trend reports, and other updates related to the data you share. Apple will not be able to access or view any of the data that you share with other Health app users.

You can view the categories of health data you choose to share with another Health app user. In the Health app, tap the Sharing tab, then tap the person you are sharing data with. You can then add and remove health topics that are shared with that person, and preview the data you’re currently sharing with them.

You can stop sharing your Health app data at any time. To do so, open the Health app, tap the Sharing tab, tap the person you want to stop sharing with, and then tap Stop Sharing. If you decide to stop sharing, the other user’s device will delete the historical data you shared with them from their Health app.

Share Health App Data with Healthcare Providers
You can select and share certain categories of Health app data, such as activity data, heart rate data, and lab results from your iPhone or iPad with a participating healthcare organization when you sign in with your account credentials for the healthcare organization. Apple and your device do not store or have access to your account credentials. You have control over the data that you share with your healthcare organization and can change what you share at any time. You can also view at any time which healthcare organizations you are sharing your Health app data with. To view and manage the sharing of your health data with a healthcare organization, open the Health app, tap the Sharing tab, then tap the healthcare organization you want to manage. Any healthcare provider with access to your patient chart at the healthcare organization can access the health data you choose to share with that healthcare organization.

Any Health app data you choose to share will be encrypted and stored by Apple on a dedicated server so that Apple can securely share this data with the healthcare organization you chose. Your data is sent from your iPhone and iPad only when the device is unlocked and connected to the internet. Apple does not maintain or have access to the encryption keys for data that is stored on our servers and shared with your healthcare organization and cannot decrypt, view, or otherwise access this data. Apple will maintain the Health app data you choose to share with your healthcare organization only for as long as necessary to support your use of this sharing feature and will use this data only to enable this sharing feature. Any health data you share in connection with this feature will be encrypted in transit and at rest when stored on Apple servers. When you use this feature, all data you choose to share with your healthcare organization that is maintained by Apple will be stored in a secure system in accordance with the Health Insurance Portability and Accountability Act of 1996 (HIPAA) privacy and security standards.

Your healthcare provider will not receive notifications when your data is available and may not see the data you share with them. Once you authorize sharing, your health records from the healthcare organization you authorize sharing with will also be automatically downloaded and stored in the Health app. Your healthcare provider may add the information you choose to share to your medical record and may also use the information you share to assist their independent assessment of your health. Any data you choose to share with your healthcare organization will be treated in accordance with that healthcare organization’s Notice of Privacy Practices and its privacy and security policies and procedures.

You can stop sharing your Health app data at any time. To do so, open the Health app, tap the Sharing tab, tap the healthcare organization you want to manage, then tap Stop Sharing. If you decide to stop sharing with a healthcare organization, they will no longer have access to your data through this feature. Any information shared with your healthcare provider prior to withdrawing access may be stored by your healthcare provider in their records.

In addition to sharing Health app data with healthcare providers, you can also separately use the Health Records feature to securely download your clinical health records from participating healthcare organizations to the Health app. Learn about Health Records on iPhone at support.apple.com/105016.

Medications

You can manage and track your medications, vitamins, and supplements within the Health app. Through the Medications feature you can create a medications list, and set up custom schedules and reminders. In certain jurisdictions, you can view educational information about your medications and receive alerts if there are potential critical interactions with medications you have added to the Medications feature. You can add medications by manually entering the information and, where available, by searching within the Health app or using the iPhone camera to add your medications. All processing for the Medications feature occurs on device. You can also use the Health Sharing features to share medications with your family, friends, and healthcare providers.

Mental Health

You can log your State of Mind and the factors contributing to it and track this information over time within the Health app through the Mental Wellbeing category, including viewing your State of Mind data in interactive charts and setting up reminders to log your state of mind. Users will also have the option to take age-appropriate standardized anxiety and depression assessments often used in clinics. All processing for Mental Health features occur on device. You can use the Health Sharing features to share State of Mind data with your family and friends. You can also scroll to Options in the Depression Risk and Anxiety Risk sections and tap Export PDF to share your depression and anxiety assessment data with healthcare providers.

Medical ID on iPhone

In the Health app on iPhone, you can create an emergency Medical ID that contains information you choose to upload about your medical conditions, allergies, medications, profile photo, and more. Show When Locked enables first responders and others to view your Medical ID when your iPhone is locked.

You can also add emergency contacts to your Medical ID. When you add emergency contacts, they are automatically alerted when you use Emergency SOS from your iPhone or from your Apple Watch if you have uninstalled the Messages app. You may also have the option to allow your Medical ID information to be sent automatically to emergency services, via a secure third-party service, when you call or text your local emergency number (for example, 911) or use Emergency SOS from your iPhone or Apple Watch. You must turn on Share During Emergency Call (where available) to automatically send your Medical ID information to emergency services when you call or text your local emergency number or use Emergency SOS. Learn more about Medical ID at support.apple.com/105072.

You can create or update your Medical ID in the Health app on iPhone. Tap your profile in the upper-right corner, tap Medical ID, then tap Get Started or Edit. You have the ability to input the amount of information that will be displayed on your Medical ID and accessible from the Lock Screen.

Vaccination Record

You can choose to securely download and store your verifiable digital vaccination record, such as your COVID-19 vaccination record, in the Health app. Your vaccination record contains information such as your name, date of birth, type of vaccine, and vaccination date(s). You can add your verifiable digital vaccination record to the Health app by obtaining your vaccination record as a QR code or digital file from the administering entity or the immunization registry in the region where you received the vaccine. When you scan the QR code or tap the file, you will be given the option to open the record in the Health app. Your verifiable digital vaccination record may also be imported and stored in the Health app through the Health Records feature if you added an account with a participating healthcare organization.

When you use a QR code or a download link to add your vaccination record to the Health app on iPhone, you can choose to add your vaccination record to Wallet, allowing you to quickly access your vaccination record from the Wallet app. When you add a vaccination card to Wallet, a copy of your vaccination record is stored by the Wallet app on the iOS device to which you added the vaccination card. The vaccination card stored in Wallet is not synced across your devices and not backed up to iCloud. The full details of your vaccination card will not be visible on the iPhone Lock Screen until you have authenticated with Face ID, Touch ID, or passcode. To present your vaccination card details, you must first authenticate. Once authenticated, anyone with access to your device may be able to view your vaccination card when displayed on your device screen so you should take precautions to protect your device.

You can remove your vaccination card from Wallet at any time. Removing your vaccination card from Wallet does not delete the copy of your vaccination record stored in the Health app. You can delete your vaccination record from the Health app at any time. Deletion of your vaccination record from the Health app will also delete the corresponding vaccination card from Wallet. Learn more about verifiable health records at support.apple.com/102467.

Accessing Your Health Data Using Siri

You can ask Siri to record certain health data types in the Health app, or to read your information available in the Health app. All processing of recognized Health app data requests by Siri occurs on device. If Siri does not recognize your request as a Health app data request, any health information you include in the request will be sent to the Siri server. You can turn off Siri’s access to your Health app data at any time by going to Settings > Apps > Health > Data Access & Devices > Siri, then tapping to turn off Access Health Data.

Removing the Health App

If you no longer want to use the Health app, you can choose to remove it from your iPhone or iPad by touching and holding the Health app on the Home Screen then tapping Remove App. When you delete the Health app on iPhone or iPad, your health data will remain on your device, and any apps or Health Sharing recipient you’ve shared health data with will continue to have access to existing health data you chose to share. Additionally, data from certain sensor-based Health features (such as Heart Rate and the Blood Oxygen app) will continue to be captured and stored on your device. You can manage your health data, including deleting your health data and revoking permissions granted to third party apps and Health Sharing recipients, in the Settings app by going to Settings > Health. If you change your mind, you can redownload the Health app from the App Store.

Retention

You remain in control over which information is added to the Health app and how long that information is stored. Your Health app data will be stored in the Health app and in iCloud if you choose to back up your health data to iCloud, for as long you choose to store your information in the Health app. You can review, edit, and delete your Health app data at any time. When you delete Health app data, certain information (such as the timestamp associated with a deleted sample) may be temporarily stored on your device to sync the deletion between your devices and with any third-party app you authorized to access your data. Learn more about managing health information in the Health app at support.apple.com/guide/iphone/view-your-health-data-iphe3d379c32/ios.

Other Information

At all times, information collected by Apple will be treated in accordance with Apple’s Privacy Policy, which can be found at www.apple.com/privacy.

Note: Some features may not be available on certain devices or in every region or language.

Published Date: September 15, 2025
